---
title: "Child test"
output: html_document
---

```{r eval=FALSE, include=FALSE, echo=TRUE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE,message=FALSE, cache=FALSE)
```

# This is the main heading

```{r eval=FALSE, include=FALSE, echo=TRUE}
library('knitr')
library('ggplot2')
library('dplyr')

## This is just an example data set
# install.packages('nycflights13')
library('nycflights13')


## The data isn't important; so use generic variable names
my.data <- flights

## Within the data, there is a set of values that I want to iterate a chunk 
## of Rmd over. Build that list of values here
looplist <- my.data %>% distinct(origin) %>% select(origin)

## Set the value to match
value.to.match <- looplist[1,]
```

Here is some text. The next `child` embed works just fine. It shows the data for the current value of the variable (`{r #  value.to.match`)

```{r child='child.Rmd'}
```

Here is some more text. Now I want to insert the child.Rmd code, but run once per value in my list, i.e. three times. 

## Using knit_expand, paste

What I'm getting is the chunk three times, but taking only the **last** value that was passed (i.e. `{r #  looplist[3,]`)

```{r include=FALSE}
out = NULL
for (i in 1:3) {
  value.to.match <- looplist[i,]
  out = c(out, knit_expand(here::here('knitr-expand', 'child.Rmd')))
}
```

`{r #  paste(knit(text = out), collapse = '\n')`
