---
title: "PBPath Journal Watch"
subtitle: "Recent Articles from PubMed"
author: "Serdar Balcı, MD, Pathologist"
date: '`r format(Sys.Date())`'
output: 
  html_notebook: 
    code_folding: hide
    highlight: kate
    number_sections: yes
    theme: cerulean
    toc: yes
    toc_float: yes
    fig_caption: yes
  html_document: 
    df_print: kable
    number_sections: yes
    toc: yes
---


# Analysis of Recent Pancreas Related Articles

Pancreas Journals
https://www.ncbi.nlm.nih.gov/nlmcatalog/?term=pancreas

Pathology Journals

Member List

DOI Link
PubMed Link
Journal Link
Altmetric API
Dimensions API


USCAP abstracts vs publication

Member list vs worldmap




```{r load required packages}
# load required packages
library(tidyverse)
library(knitr)
library(rstudioapi)
```

    
```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE, tidy = TRUE)
```



```{r}
myTerm <- rstudioapi::terminalCreate(show = FALSE)
rstudioapi::terminalSend(myTerm, "esearch -db pubmed -query 'pancreas[Title/Abstract]) AND pathology' -datetype EDAT -min 2018/05/01 -max 3000 | \
efetch -format xml | \
xtract -pattern PubmedArticle -element MedlineCitation/PMID \
-block ArticleId -if ArticleId@IdType -equals doi -element ArticleId &> myquery.txt")
Sys.sleep(1)
repeat{
    Sys.sleep(0.1)
    if(rstudioapi::terminalBusy(myTerm) == FALSE){
        print("Code Executed")
        break
    }
}
```


```{r}
readLines("myquery.txt")
```



Pathology Journal ISSN List was retrieved from [In Cites Clarivate](https://jcr.incites.thomsonreuters.com/), and Journal Data Filtered as follows: `JCR Year: 2016 Selected Editions: SCIE,SSCI Selected Categories: 'PATHOLOGY' Selected Category Scheme: WoS`

```{r Get ISSN List from data downloaded from WoS}
# Get ISSN List from data downloaded from WoS
ISSNList <- JournalHomeGrid <- read_csv("data/JournalHomeGrid.csv",
                                        skip = 1) %>%
    select(ISSN) %>%
    filter(!is.na(ISSN)) %>%
    t() %>%
    paste("OR ", collapse = "") # add OR between ISSN List

ISSNList <- gsub(" OR $","" ,ISSNList) # to remove last OR
```

Data is retrieved from PubMed via E-direct.

PubMed collection from National Library of Medicine (https://www.ncbi.nlm.nih.gov/pubmed/), has the most comprehensive information about peer reviewed articles in medicine.
The API (https://dataguide.nlm.nih.gov/) is available for getting and fetching data from the server.

The query for PubMed is generated as "ISSN List AND keywords" like done in [advanced search of PubMed](https://www.ncbi.nlm.nih.gov/pubmed/advanced).


```{r Generate Search Formula For Pathology Journals AND Countries}
# Generate Search Formula For Pathology Journals AND Countries
searchformulaTR <- paste("'",ISSNList,"'", " AND ", "Turkey[Affiliation]")
searchformulaDE <- paste("'",ISSNList,"'", " AND ", "Germany[Affiliation]")
searchformulaJP <- paste("'",ISSNList,"'", " AND ", "Japan[Affiliation]")
```



From the fetched data articles are grouped by country and keywords.

```{r Articles per countries per year}
# Articles per countries per year
tableTR <- table(YearPubmed(fetchTurkey)) %>%
    as_tibble() %>%
    rename(Turkey = n, Year = Var1)

tableDE <- table(YearPubmed(fetchGermany)) %>%
    as_tibble() %>%
    rename(Germany = n, Year = Var1)

tableJP <- table(YearPubmed(fetchJapan)) %>%
    as_tibble() %>%
    rename(Japan = n, Year = Var1)

# Join Tables
articles_per_year_table <- list(
    tableTR,
    tableDE,
    tableJP
) %>%
    reduce(left_join, by = "Year", .id = "id")

```


```{r Prepare table for output}
# Prepare table for output
articles_per_year <- articles_per_year_table %>%
    gather(Country, n, 2:4)

articles_per_year$Country <- factor(articles_per_year$Country,
                                    levels =c("Japan", "Germany", "Turkey"))
```


**Result:**


```{r Print the Table of Articles per year per country, echo=FALSE}
# Print the Table of Articles per year, per country
knitr::kable(articles_per_year_table, caption = "Table of Articles per year, per country")
```

mapgraph



And the figure below shows this data in a line graph.


---




# Feedback

[Serdar Balcı, MD, Pathologist](https://github.com/sbalci) would like to hear your feedback: https://goo.gl/forms/YjGZ5DHgtPlR1RnB3

This document will be continiously updated and the last update was on `r Sys.Date()`.

---

# Back to Main Menu

[Main Page for Bibliographic Analysis](https://sbalci.github.io/pubmed/BibliographicStudies.html)












