---
title: "Cancer Packages"
---

# BCRA

https://cran.r-project.org/web/packages/BCRA/index.html


# cgdsr

cgdsr: R-Based API for Accessing the MSKCC Cancer Genomics Data Server (CGDS)

https://cran.r-project.org/web/packages/cgdsr/index.html


# TCGAbiolinksGUI

```{r eval=FALSE, include=FALSE, echo=TRUE}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install("TCGAbiolinksGUI", version = "3.8")
```

```{r eval=FALSE, include=FALSE, echo=TRUE}
browseVignettes("TCGAbiolinksGUI")
```

https://bioconductor.org/packages/release/bioc/html/TCGAbiolinksGUI.html

```{r eval=FALSE, include=FALSE, echo=TRUE}
library(TCGAbiolinksGUI)
TCGAbiolinksGUI()
```



# RTCGA


```{r eval=FALSE, include=FALSE, echo=TRUE}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install("RTCGA", version = "3.8")
```

```{r eval=FALSE, include=FALSE, echo=TRUE}
browseVignettes("RTCGA")
```

```{r eval=FALSE, include=FALSE, echo=TRUE}
RTCGA::infoTCGA()
```


# CancerSubtypes


```{r eval=FALSE, include=FALSE, echo=TRUE}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install("CancerSubtypes", version = "3.8")
```



```{r eval=FALSE, include=FALSE, echo=TRUE}
browseVignettes("CancerSubtypes")
```



# CancerMutationAnalysis


# cancerclass


# canceR

```{r eval=FALSE, include=FALSE, echo=TRUE}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install("canceR", version = "3.8")
```

```{r eval=FALSE, include=FALSE, echo=TRUE}
browseVignettes("canceR")
```

```{r eval=FALSE, include=FALSE, echo=TRUE}
canceR::canceR()
```


# bioCancer

```{r eval=FALSE, include=FALSE, echo=TRUE}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install("bioCancer", version = "3.8")
```

```{r eval=FALSE, include=FALSE, echo=TRUE}
browseVignettes("bioCancer")
```

```{r eval=FALSE, include=FALSE, echo=TRUE}
bioCancer::bioCancer()
```



# TCGAretriever

TCGAretriever: Retrieve Genomic and Clinical Data from TCGA


https://cran.r-project.org/web/packages/TCGAretriever/index.html

# TCGA2STAT

https://cran.r-project.org/web/packages/TCGA2STAT/vignettes/TCGA2STAT.html


# TCIApathfinder

TCIApathfinder: Client for the Cancer Imaging Archive REST API


https://cran.r-project.org/web/packages/TCIApathfinder/index.html


# MILC

MILC: MIcrosimulation Lung Cancer (MILC) model

https://cran.r-project.org/web/packages/MILC/index.html

# InfiniumPurify


InfiniumPurify: Estimate and Account for Tumor Purity in Cancer Methylation Data Analysis

https://cran.r-project.org/web/packages/InfiniumPurify/index.html


