---
title: "My R Codes For Data Analysis"
subtitle: "In this repository I am going to collect `R codes` for data analysis. Codes are from various resources and I try to give original link as much as possible."
author: "[Serdar Balcı, MD, Pathologist](https://www.serdarbalci.com/)"
date: '`r format(Sys.Date())`'
output: 
  html_notebook: 
    fig_caption: yes
    highlight: tango
    number_sections: yes
    theme: paper
    toc: yes
    toc_depth: 5
    toc_float: yes
  html_document: 
    code_folding: hide
    df_print: kable
    keep_md: yes
    number_sections: yes
    theme: cerulean
    toc: yes
    toc_float: yes
    highlight: kate
---


## File organization best practices

This page summarises how to organize files and analysis before everything gets jumbled up:
[Setting up a reproducible data analysis workflow in R](https://andrewbtran.github.io/NICAR/2018/workflow/docs/01-workflow_intro.html)

Basically they suggest:
- using a project and project folder in RStudio for each analysis
- using `packrat` as much as possible

`setwd()` and `getwd()` is not necesary when you use projects.



---

- **Why should I use the here package when I'm already using projects?**

https://malco.io/2018/11/05/why-should-i-use-the-here-package/


```{r}
library(here)
here()
```

```{r}
dr_here()
```

```{r}
here("figure", "figure.png")
```

```{r}
file.path("figure", "figure.png")
```

```{r}
read_csv(here("data", "mtcars.csv"))
```

