---
title: "My R Codes For Data Analysis"
---


## File organization best practices

This page summarises how to organize files and analysis before everything gets jumbled up:
[Setting up a reproducible data analysis workflow in R](https://andrewbtran.github.io/NICAR/2018/workflow/docs/01-workflow_intro.html)

Basically they suggest:
- using a project and project folder in RStudio for each analysis
- using `packrat` as much as possible

`setwd()` and `getwd()` is not necesary when you use projects.



---

- **Why should I use the here package when I'm already using projects?**

https://malco.io/2018/11/05/why-should-i-use-the-here-package/


```{r eval=FALSE, include=FALSE, echo=TRUE}
library(here)
here()
```

```{r eval=FALSE, include=FALSE, echo=TRUE}
dr_here()
```

```{r eval=FALSE, include=FALSE, echo=TRUE}
here("figure", "figure.png")
```

```{r eval=FALSE, include=FALSE, echo=TRUE}
file.path("figure", "figure.png")
```

```{r eval=FALSE, include=FALSE, echo=TRUE}
read_csv(here("data", "mtcars.csv"))
```

