---
title: "My R Codes For Data Analysis"
subtitle: "Getting Data into R"
author: "[Serdar Balcı, MD, Pathologist](https://www.serdarbalci.com/)"
date: '`r format(Sys.Date())`'
output: 
  html_notebook: 
    fig_caption: yes
    highlight: tango
    number_sections: yes
    theme: paper
    toc: yes
    toc_depth: 5
    toc_float: yes
  html_document: 
    code_folding: hide
    df_print: kable
    keep_md: yes
    number_sections: yes
    theme: cerulean
    toc: yes
    toc_float: yes
    highlight: kate
---

# Getting Data into R / Veriyi R'a yükleme

## Import Data

### Import using RStudio

### Import CSV File

```{r}
scabies <- read.csv(file = "http://datacompass.lshtm.ac.uk/607/2/S1-Dataset_CSV.csv", header = TRUE, sep = ",")
scabies
```


#### How to import multiple .csv files at once?

https://stackoverflow.com/questions/11433432/how-to-import-multiple-csv-files-at-once


```
temp = list.files(pattern="*.csv")
myfiles = lapply(temp, read.delim)

temp = list.files(pattern="*.csv")
for (i in 1:length(temp)) assign(temp[i], read.csv(temp[i]))

temp = list.files(pattern="*.csv")
list2env(
  lapply(setNames(temp, make.names(gsub("*.csv$", "", temp))), 
         read.csv), envir = .GlobalEnv)

```


```
# Get the files names
files = list.files(pattern="*.csv")
# First apply read.csv, then rbind
myfiles = do.call(rbind, lapply(files, function(x) read.csv(x, stringsAsFactors = FALSE)))
```

```
library(data.table)
DT = do.call(rbind, lapply(files, fread))
# The same using `rbindlist`
DT = rbindlist(lapply(files, fread))
```

```
library(readr)
library(dplyr)
tbl = lapply(files, read_csv) %>% bind_rows()
```






### Import TXT File

```{r}
ebola <- read.csv(file = "http://datacompass.lshtm.ac.uk/608/1/mmc1.txt", header = TRUE, sep = ",")
ebola
```


### Import Excel File

```
my_data <- read_excel(file.choose())


files <- list.files(pattern = ".xlsx")

data_xlsx_df <- map_df(set_names(files), function(file) {
  file %>% 
    excel_sheets() %>% 
    set_names() %>% 
    map_df(
      ~ read_xlsx(path = file, sheet = .x, range = "H3"),
      .id = "sheet")
}, .id = "file")
```

#### Import Sheets

<!-- # Sheets -->

<!-- library(tidyverse) -->
<!-- library(readxl) -->


<!-- path <- "ICPN_RAW.xls" -->
<!-- sheetlist <- path %>%  -->
<!--     excel_sheets() %>%  -->
<!--     set_names() %>%  -->
<!--     map(read_excel, skip = 1, path = path) -->

<!-- sheetlist <- sheetlist[-29] -->


<!-- sheetlist <- sheetlist %>% -->
<!--     reduce(left_join, by = "Respondant", .id = "id", suffix = c("1","2")) -->

<!-- names(sheetlist) -->

<!-- columnNames <- c( -->
<!--     "ID", -->
<!--     "DX", -->
<!--     "y/n", -->
<!--     "~plastic", -->
<!--     "WHO- 2010 classification", -->
<!--     "GRADE", -->
<!--     "INVASIVE CA", -->
<!--     "CELL LINEAGE", -->
<!--     "IPMN Lineage (PRE/MIN)", -->
<!--     "experience with this invasion", -->
<!--     "COMMENTS" -->
<!-- ) -->

<!-- columnNumbers <- rep(c(1:28), each = 11) -->

<!-- columnNames2 <- paste(columnNames, columnNumbers, sep = "") -->

<!-- columnNames2 <- c("Respondant", columnNames2) -->

<!-- names(sheetlist) <- columnNames2 -->



<!-- # "Respondant"	"ID"	"y/n"	"WHO- 2010 classification"	"GRADE"	"INVASIVE CA"	"CELL LINEAGE"	"IPMN Lineage (PRE/MIN)" -->

<!-- deneme <- sheetlist %>%  -->
<!--     select(starts_with("Respondant"), starts_with("GRADE")) -->







<!-- # deneme[deneme=="HIGH"] <- 3 -->
<!-- # deneme[deneme=="HIGH (focal)"] <- 3 -->
<!-- # deneme[deneme=="MODERATE"] <- 2 -->
<!-- # deneme[deneme=="LOW"] <- 1 -->
<!-- #  -->
<!-- # deneme <- as.data.frame(deneme) -->
<!-- #  -->
<!-- # row.names(deneme) <- deneme$Respondant -->
<!-- #  -->
<!-- # deneme <- deneme[-1] -->
<!-- #  -->
<!-- # deneme[is.na(deneme)] <- 1 -->
<!-- #  -->
<!-- # deneme <- map_df(deneme, as.matrix) -->
<!-- #  -->
<!-- # glimpse(deneme) -->
<!-- #  -->
<!-- # heatmap(deneme) -->

<!-- write_csv(deneme, "deneme.csv") -->






### Import SPSS File

### Keep SPSS labels

```{r}
library(foreign) # foreign paketi yükleniyor
```

read.spss komutu ile değer etiketlerini almasını ve bunu liste olarak değil de data.frame olarak kaydetmesini istiyoruz

```{r}
mydata <- read.spss("mydata.sav", use.value.labels = TRUE, to.data.frame = TRUE)
```

aktardığımız data.frame'in özellikleri (attr) içinde değişkenlerin etiketleri var, bunları dışarı çıkartıyoruz

```{r}
VariableLabels <- as.data.frame(attr(mydata, "variable.labels"))
```


elde ettiğimiz data.frame'deki satır isimleri değişkenlerin isimleri oluyor, karşılarında da değişken etiketleri var
satır isimlerini de dışarı çıkartıyoruz

```{r}
VariableLabels$original <- rownames(VariableLabels)
```

Değişken etiketi olanları etiketleri ile diğerlerini olduğu gibi saklıyoruz  

```{r}
VariableLabels$label[VariableLabels$label ==""] <- NA 
VariableLabels$colname <- VariableLabels$original
VariableLabels$colname[!is.na(VariableLabels$label)] <- as.vector(VariableLabels$label[!is.na(VariableLabels$label)])
```

son olarak da data.frame'deki sütun isimlerini değiştiriyoruz

```{r}
names(mydata) <- VariableLabels$colname
```





# Export Data

### Export to SPSS, while keeping labels

R'da `factor` olan label verdiğiniz değişkenleri `SPSS` ya da diğer istatistik programlarına aktardığınızda bu tanımlamaları korumak işimize yarar. Bunun için `foreign` paketi ile bir `txt` dosyası ve bir `sps` dosyası oluşturuyoruz. SPSS'te `sps` dosyasını açıp kodu çalıştırarak tekrar atanan değerler geri yükleniyor.


```{r}
library(foreign)
write.foreign(mydata, "mydata.txt", "mydata.sps",   package = "SPSS")
```


---

https://twitter.com/WeAreRLadies/status/1034817323922804737

```
f <- list.files( "my_folder", pattern = "*.csv", full.names = TRUE)
d <- purrr::map_df(f, readr::read_csv, .id = "id")
```

---

```
m <- lm(mpg ~ qsec + wt, data = mtcars)
broom::tidy(m)
```

---

Import a Directory of CSV Files at Once Using {purrr} and {readr}

https://www.gerkelab.com/blog/2018/09/import-directory-csv-purrr-readr/

```
data_dir %>% 
  dir_ls(regexp = "\\.csv$") %>% 
  map_dfr(read_csv, .id = "source") %>% 
  mutate(Month_Year = myd(Month_Year, truncated = 1))
```  


---

https://suatatan.wordpress.com/2017/10/07/bulk-replacing-turkish-characters-in-r/

Turkish character sometimes became the menace for the data scientist. To avoid the risks you may want to change it with safe characters. To do that you can use this code:

```
#turkce karakter donusumu
to.plain <- function(s) {

# 1 character substitutions
old1 <- “çğşıüöÇĞŞİÖÜ”
new1 <- “cgsiuocgsiou”
s1 <- chartr(old1, new1, s)

# 2 character substitutions
old2 <- c(“œ”, “ß”, “æ”, “ø”)
new2 <- c(“oe”, “ss”, “ae”, “oe”)
s2 <- s1
for(i in seq_along(old2)) s2 <- gsub(old2[i], new2[i], s2, fixed = TRUE)

s2
}
df$source=as.vector(sapply(df$source,to.plain))


to.plain(make.names(tolower(names(df))))
```


- Remove all special characters from a string in R?

https://stackoverflow.com/questions/10294284/remove-all-special-characters-from-a-string-in-r

```
x <- "a1~!@#$%^&*(){}_+:\"<>?,./;'[]-="
stringr::str_replace_all(x, "[[:punct:]]", " ")
stringr::str_replace_all(x, "[^[:alnum:]]", " ")
```

```
astr <- "Ábcdêãçoàúü"
iconv(astr, from = 'UTF-8', to = 'ASCII//TRANSLIT')
```

```
Data  <- gsub("[^0-9A-Za-z///' ]","'" , Data ,ignore.case = TRUE)

Data <- gsub("''","" , Data ,ignore.case = TRUE)
```





# pdftables

https://cran.r-project.org/web/packages/pdftables/vignettes/convert_pdf_tables.html


# tabulizer

Extract Tables from PDFs


https://github.com/ropensci/tabulizer



# rio

Import, Export, and Convert Data Files

https://thomasleeper.com/rio/index.html

https://cran.r-project.org/web/packages/rio/vignettes/rio.html


# read with purrr


R tip: Iterate with purrr's map_df function


https://www.infoworld.com/video/89075/r-tip-iterate-with-purrrs-map-df-function



# The janitor package

https://garthtarr.github.io/meatR/janitor.html

```{r}
# install.packages("janitor")
```

```{r}
library(tidyverse)
library(janitor)
library(xlsx)
```

```{r}
# mymsa <-  data.table::fread("https://garthtarr.com/data/mymsa.xlsx", fill = TRUE)
mymsa <-  read_excel("data/mymsa.xlsx")
mymsa$çğşüö <- 2
x <-  janitor::clean_names(mymsa)
```


```{r}
data.frame(mymsa = colnames(mymsa), x = colnames(x))
```


```{r}
tabyl(x, meat_colour) %>%
  knitr::kable()
```



```{r}
table(x$meat_colour)
```


```{r}
# Load dplyr for the %>% pipe 
library(dplyr)
x %>% tabyl(meat_colour) %>%
  knitr::kable()
```


```{r}
x %>% 
  tabyl(meat_colour) %>% 
  adorn_pct_formatting(digits = 0, affix_sign = TRUE) %>%
  knitr::kable()
```



```{r}
x %>% tabyl(spare)
```



```{r}
x = remove_empty(x, which = c("rows","cols"))
```



```{r}
x = read_excel("data/mymsa.xlsx") %>% 
  clean_names() %>% remove_empty()
```


```{r}
x %>% tabyl(meat_colour, plant) %>%
  knitr::kable()

# can also make 3 way tables
```




```{r}
# row totals
x %>% 
  tabyl(meat_colour, plant) %>% 
  adorn_totals(where = "row") %>%
  knitr::kable()
```

  

```{r}
# column totals
x %>% 
  tabyl(meat_colour, plant) %>% 
  adorn_totals(where = "col") %>%
  knitr::kable()
```




```{r}
# row and column totals
x %>% 
  tabyl(meat_colour, plant) %>% 
  adorn_totals(where = c("row","col"))
```
  
  
  
```{r}
x %>% 
  tabyl(meat_colour, plant) %>% 
  adorn_totals(where = c("row","col")) %>% 
  adorn_percentages(denominator = "col") %>% 
  adorn_pct_formatting(digits = 0) 
```

  
```{r}
x %>% 
  tabyl(meat_colour, plant) %>% 
  adorn_totals(where = c("row","col")) %>% 
  adorn_percentages(denominator = "col") %>% 
  adorn_pct_formatting(digits = 0) %>% 
  adorn_ns(position = "front")
```


```{r}
adorn_cumulative <- function(dat, colname, dir = "down"){

  if(!missing(colname)){
    colname <- rlang::enquo(colname)
  } else if("valid_percent" %in% names(dat)) {
  colname <- rlang::sym("valid_percent")
  } else if("percent" %in% names(dat)){
    colname <- rlang::sym("percent")
  } else {
    stop("\"colname\" not specified and default columns valid_percent and percent are not present in data.frame dat")
  }

  target <- dplyr::pull(dat, !! colname)

  if(dir == "up"){
    target <- rev(target)
  }
  dat$cumulative <- cumsum(ifelse(is.na(target), 0, target)) + target*0 # an na.rm version of cumsum, from https://stackoverflow.com/a/25576972
  if(dir == "up"){
    dat$cumulative <- rev(dat$cumulative)
    names(dat)[names(dat) %in% "cumulative"] <- "cumulative_up"
  }
  dat
}
```





  

```{r}
x %>% get_dupes(rfid)
```
  

```{r}
x1 = x %>% slice(1:3)
x2 = bind_rows(x1,x)
x2 %>% get_dupes(rfid)
```

  

## convert excel number into date


```{r}
janitor::excel_numeric_to_date(41103)
```









