

```
output:
  pdf_document: default
  html_document: default
header-includes:
- \usepackage{pdflscape}
- \usepackage{xcolor}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
```


# ggplot2 ----

mpg



```{r, background='#fff5e6'}
library("tidyverse")
ggplot(mpg) + 
    geom_point(aes(x = displ, y = hwy))
```



ggplot(mpg, aes(model, manufacturer)) + geom_point()



ggplot(mpg, aes(displ, cty, colour = year)) + 
    geom_point()



ggplot(mpg, aes(displ, hwy)) + 
    geom_point(aes(shape = year))


ggplot(mpg, aes(displ, hwy)) + 
    geom_point() + 
    geom_smooth(span = 0.2)



ggplot(mpg, aes(hwy)) +
    geom_histogram() +
    geom_freqpoly()




ggplot(mpg, aes(cty, hwy)) + 
    geom_point() +
    geom_smooth()


ggplot(mpg, aes(class, hwy)) + geom_boxplot()
ggplot(mpg, aes(reorder(class, hwy), hwy)) + geom_boxplot()


# gganimate ----



library(gganimate)

p <- ggplot(iris, aes(x = Petal.Width, y = Petal.Length)) + 
    geom_point()

plot(p)


anim <- p + 
    transition_states(Species,
                      transition_length = 2,
                      state_length = 1)

anim


p + 
    enter_appear()




```{r eval=FALSE, include=FALSE, echo=TRUE}
sometext <-strsplit(
    paste0("You can even try to make some crazy things like this paragraph. ","It may seem like a useless feature right now but it's so cool ","and nobody can resist. ;)"), " ")[[1]]

text_formatted <-paste(
    kableExtra::text_spec(sometext,
              "latex",
              color = kableExtra::spec_color(1:length(sometext), end = 0.9),
              font_size =kableExtra::spec_font_size(1:length(sometext), begin = 5, end = 20)),collapse = " ")

mytext <-  kableExtra::text_spec("Serdar", color = "blue", background = "black")

```


`{r #  mytext`


To display the text, type `{r #  text_formatted` outside of the chunk




```{r eval=FALSE, include=FALSE, echo=TRUE}

library(kableExtra)

my_text <- paste0("İstatistik Metod:",
"Sürekli verilerin ortalama, standart sapma, median, minimum ve maksimum değerleri verildi.",

"R Core Team (2019). R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria. URL https://www.R-project.org/.",
  
"Therneau T (2015). A Package for Survival Analysis in S. version 2.38, URL:https://CRAN.R-project.org/package=survival",

"Terry M. Therneau, Patricia M. Grambsch (2000). Modeling Survival Data: Extending the Cox Model. Springer, New York. ISBN 0-387-98784-3.",

"Ewen Harrison, Tom Drake and Riinu Ots (2019). finalfit: Quickly Create Elegant Regression Results Tables and Plots when Modelling. R package version 0.9.6. https://github.com/ewenharrison/finalfit",

sep = "\n"
)

my_text <- paste0(
  "You can even try to make some crazy things like this paragraph. ",
  "It may seem like a useless feature right now but it's so cool ",
  "and nobody can resist. ;)")


my_text_html <- paste(
  text_spec(
    my_text,
    "html",
    color = "red",
    background = "yellow"
    ),
  collapse = " ")



sometext <-strsplit(my_text, " ")[[1]]

my_text_latex <- paste(
  text_spec(
    sometext,
    "latex",
    color = "red",
    background = "yellow"
    ),
  collapse = " ")


```



`r #  my_text_html`


`r #  my_text_latex`




