---
title: "How to Prepare Data for Histopathology Research?"
author: '[Serdar Balcı, MD, Pathologist](https://sbalci.github.io/)'
date: "`r format(Sys.Date())`"
output:
  revealjs::revealjs_presentation:
    incremental: yes
    theme: sky
    highlight: pygments
    center: no
    smart: yes
    transition: fade
    self_contained: yes
    ig_width: 7
    fig_height: 6
    fig_caption: yes
    reveal_options:
      slideNumber: yes
      previewLinks: yes
  prettydoc::html_pretty:
    theme: leonids
    highlight: github
  rmdshower::shower_presentation: null
  beamer_presentation:
    incremental: yes
    highlight: tango
  html_notebook:
    fig_caption: yes
    highlight: kate
    number_sections: yes
    theme: flatly
    toc: yes
    toc_depth: 5
    toc_float: yes
  slidy_presentation: null
  pdf_document:
    toc: yes
    toc_depth: '5'
  html_document:
    fig_caption: yes
    keep_md: yes
    toc: yes
    toc_depth: 5
    toc_float: yes
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      beforeInit:
      - macros.js
      - https://platform.twitter.com/widgets.js
      highlightStyle: github
      highlightLines: yes
      countIncrementalSlides: no
    self_contained: yes
  ioslides_presentation:
    incremental: yes
    highlight: github
institute: '[serdarbalci.com](https://www.serdarbalci.com)'
editor_options:
  chunk_output_type: inline
---

<!-- Open all links in new tab-->  
<base target="_blank"/>  


<!-- Go to www.addthis.com/dashboard to customize your tools --> <script type="text/javascript" src="//s7.addthis.com/js/300/addthis_widget.js#pubid=ra-5bc36900a405090b">  
</script>



```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width = 12, fig.height = 8, fig.path = 'Figs/', echo = FALSE, warning = FALSE, message = FALSE, error = FALSE, eval = TRUE, tidy = TRUE, comment = NA, cache = TRUE)
```


```{r strings , include=FALSE}
PubMedString <- "PubMed: https://www.ncbi.nlm.nih.gov/pubmed/?term="

doiString <- "doi: https://doi.org/"

dimensionString1 <- "<script async='' charset='utf-8' src='https://badge.dimensions.ai/badge.js'></script> <span class='__dimensions_badge_embed__' data-doi='"

dimensionString2 <- "' data-style='small_circle' data-hide-zero-citations='true' data-legend='always'></span>"

altmetricString1 <-"<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script> <span class='altmetric-embed' data-link-target='_blank' data-badge-details='right' data-badge-type='donut' data-doi='"

altmetricString2 <- "' data-hide-no-mentions='true'></span>"

addthis_String1 <- "<div class='addthis_inline_share_toolbox' data-url='pbpath.org/current-journal-watch/' data-title='See this abstract on #PBPath #JournalWatch : "

addthis_String2 <- "'></div>"

```


```{r run xaringan, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
# xaringan::inf_mr()
# servr::daemon_stop(1)
```


# How to Prepare Data for Histopathology Research?

**Outline**

- Why is Data Preparation Important?
- Do I need a specific Software?
- What are the Golden Rules?
- What do I do with Data after analysis?
- I got all the tables from the biostatistician, is it enough?
- What is a Good (Clean/Ideal/Tidy) Data?
- What is a Bad (Dirty/Common/Untidy) Data?
- Do I need to know statistics before collecting Data?
- Do I need to have a hypothesis before collecting Data?
- Do I need a research question before collecting Data?


---


# How to Prepare Data for Histopathology Research?

**We Should Collect the Data Related to What We will Report**

- Recommendations for reporting histopathology studies: a proposal

```{r 25846513, include=FALSE}

PMID_25846513 <- RefManageR::ReadPubMed('25846513', database = 'PubMed')

citation_25846513 <- paste0(PMID_25846513$journal,' ', PMID_25846513$year, ' ', PMID_25846513$month,';', PMID_25846513$volume,'(', PMID_25846513$number,'):', PMID_25846513$pages)

PubMed_25846513 <- paste0(PubMedString, PMID_25846513$eprint)

doi_25846513 <- paste0(doiString, PMID_25846513$doi)

dimensionBadge_25846513 <- paste0(dimensionString1, PMID_25846513$doi,dimensionString2)

altmetricBadge_25846513 <- paste0(altmetricString1, PMID_25846513$doi, altmetricString2 )

addthis_inline_25846513 <- paste0(addthis_String1, PMID_25846513$title , " PMID: 25846513" , addthis_String2)
```

<!-- <details open> <summary> -->
- **`r PMID_25846513$title`**
<!-- </summary>  -->

*`r citation_25846513`*

`r PubMed_25846513`

`r addthis_inline_25846513`

`r PMID_25846513$abstract`

`r doi_25846513`

`r dimensionBadge_25846513`

`r altmetricBadge_25846513`

<!-- </details> -->


---


# Tables and Graphs to be Formed  

- Table One: Clinical Features Related to this disease and Histopathological Features (like a CAP synoptic)

- Cross Tables

- IHC Tables

- Survival Tables and Graphs



---

# Age


---


# Gender

- Male
- Female
- Non-binary (based on research)

For missing values:

{gender} 📦

https://lincolnmullen.com/software/gender/

https://github.com/ropensci/gender



---

# Surgery Type

---








