--- 
title: "My R Codes for Data Analysis"
author: "Serdar Balcı"
date: "`{r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: ['bib/book.bib', 'bib/packages.bib']
biblio-style: apalike
link-citations: yes
description: "This is a collection of R codes I use for data analysis"
always_allow_html: true
---

# Preface

```{r echo=TRUE}
# install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```


```{r echo=TRUE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'bib/packages.bib')
```


UNDER CONSTRUCTION 🛠⛔️⚠️🔩

This repository is a draft version of many different codes. Organizing
them will take some time. That is why I have started a template
repository on GitHub.

<https://github.com/sbalci/histopathology-template/>  
<https://sbalci.github.io/histopathology-template/>

These templates will allow me to make histopathology research data
analysis easier and more standard.

-----

Bir sonraki R-project sunumuna şu linkten belirtilen gün ve saatte
erişebilirsiniz.

Bir sonraki sunum:  
R, RStudio ve RMarkdown ile Tekrarlanabilir Rapor  
Join Zoom Meeting  
<https://us04web.zoom.us/j/808337924>  
Meeting ID: 808 337 924

Sunum linkleri:  
<https://sbalci.github.io/MyRCodesForDataAnalysis/R-Markdown.nb.html>  
<https://sbalci.github.io/MyRCodesForDataAnalysis/R-Markdown.html>

25 Eylül 2019  
<https://youtu.be/GZ85WE9f2R0>  
<https://sbalci.github.io/MyRCodesForDataAnalysis/R-Giris.html>  
<https://sbalci.github.io/MyRCodesForDataAnalysis/R-Giris.nb.html>

Anonim Geri Bildirim:  
<https://goo.gl/forms/YjGZ5DHgtPlR1RnB3>

# Lecture Notes

## Introduction

[R-Giris](https://sbalci.github.io/MyRCodesForDataAnalysis/R-Giris.nb.html)
[R-Giris
Sunum](https://sbalci.github.io/MyRCodesForDataAnalysis/R-Giris.html)

[R-Arayuzler](https://sbalci.github.io/MyRCodesForDataAnalysis/R-Arayuzler.nb.html)

[Where To Learn
R](https://sbalci.github.io/MyRCodesForDataAnalysis/WhereToLearnR.nb.html)

## Use R Markdown

[R-Markdown](https://sbalci.github.io/MyRCodesForDataAnalysis/R-Markdown.nb.html)

[R-Markdown
Sunum](https://sbalci.github.io/MyRCodesForDataAnalysis/R-Markdown.html)

-----

# My R Codes For Data Analysis

[![HitCount](http://hits.dwyl.io/sbalci/MyRCodesForDataAnalysis.svg)](http://hits.dwyl.io/sbalci/MyRCodesForDataAnalysis)
[![Say
Thanks\!](https://img.shields.io/badge/Say%20Thanks-!-1EAEDB.svg)](https://saythanks.io/to/sbalci)

In this repository I am going to collect `R codes` for data analysis.

The title says “My R Codes” but I am only the collector. I will try to
refer the original sources as far as I can. [Serdar Balci, MD,
Pathologist](https://www.serdarbalci.com/)

**My aim** is to collect all the codes one needs, where one starts with
an excel or spss file and then end with the most common analysis used in
histopathology papers : *[example
table](https://media.nature.com/original/nature-assets/modpathol/journal/v31/n1/extref/modpathol2017106x4.docx)*

There are plenty of ways to do an analysis in `R`, which is great but
also confusing for the newbies. I will collect the codes here so that I
can refer later and then update them as I learn more.

**See the links for the Codes below:**

-----

WorldBankCountryAnalysis.R 1 cards.R 2 DataCamp.R 3 GABAHip.R 4
googleCite.R 5 makenames.R 6 R-Program-Env-1-2.R 8 SurvivalAnalysis.R 9
SurvivalAnalysisR.R 10 tangram.R 11 TurkPathScholar.R deneme.R
geom\_bartext.R gilbert-dahl.R GitHubUpdateV2.R
join-animations-with-gganimate.R plumber.R plumberRun.R
power\_multiplot.R quRan-data-raw-clean\_data.R
Retrieve\_pubmed\_citation\_data.R sf\_transitions.R silge.R

-----

12 ArticlesPerJournalsPerCountry.Rmd 13 CountryBasedComparison.Rmd 14
JournalWatchPBPath.Rmd 15
MeSH\_Terms\_Pathology\_Articles\_From\_Turkey.Rmd 16 6-tables.Rmd
arsenal.Rmd AutomatedDashboardDeviation.Rmd Autoreport.Rmd bbplot.Rmd
Bibliography.Rmd bioconductor.Rmd Biyoinformatik.Rmd CancerInSilico.Rmd
CancerPackages.Rmd CloudForResearch.Rmd codes.Rmd CompareMeans.Rmd
CompareProportions.Rmd ContingencyTables.Rmd Correlations.Rmd
DataList.Rmd DataScienceLiveBook.Rmd datatable.Rmd DataTools.Rmd
DecisionTreeKararAgaci.Rmd DescriptiveStatistics.Rmd drive.Rmd
edirect-addin.Rmd eurostat.Rmd EvidenceSynthesisProjects.Rmd
ExplatoryDataAnalysisSummaryStatistics.Rmd FileOrganization.Rmd
finalfit.Rmd finalfit2.Rmd FlippingCoin.Rmd formattable.Rmd Formulas.Rmd
GeneralLinearModels.Rmd GeneralResources.Rmd GettingDataVeriYukleme.Rmd
GitHub.Rmd githubdocument.Rmd googledrive-trial.Rmd GoogleScholar.Rmd
Graphs.Rmd h2o.Rmd HierarchicalClustering.Rmd
HistopathologyResearchTemplate.Rmd How-To-Use-R-With-Excel.Rmd
htmlclean.Rmd htmldocco.Rmd huxtable.Rmd HypothesisTesting.Rmd keras.Rmd
KMeansClustering.Rmd lessR.Rmd LinearRegression.Rmd MachineLearning.Rmd
material.Rmd MultiplePages.Rmd mxnet.Rmd news.Rmd Ninja.Rmd OpenCPU.Rmd
papeR.Rmd papeR2.Rmd Power\_Analysis.Rmd power.Rmd PowerAnalysis.Rmd
PrepareData.Rmd PythonPandas.Rmd R-Arayuzler.Rmd R-Giris.Rmd R-Tipps.Rmd
radix.Rmd rchess.Rmd readthedown.Rmd Regression.Rmd reprex.Rmd
ReproducibleResearch.Rmd RISmed.Rmd RinPathologyResearch.Rmd
rmarkdown\_websites\_tutorial.Rmd rmarkdown\_websites\_tutorial2.Rmd
ROC.Rmd rorcid.Rmd RPackagesUsed.Rmd SankeyDiagrams.Rmd
SensitivitySpecificity.Rmd shiny.Rmd ShinyCodes.Rmd snahelper.Rmd
summarytools\_introduction.Rmd summarytools\_markdown.Rmd
survival\_analysis\_in\_r\_tutorial.Rmd
survival\_analysis\_in\_r\_tutorial2.Rmd SurvivalAnalysis.Rmd
SyncingGitHubFork.Rmd Table.Rmd tensorflow.Rmd TextMining.Rmd
the-lesser-known-stars-of-the-tidyverse.Rmd tuftedoc.Rmd Tutorials.Rmd
tweetbook1.Rmd Twitter.Rmd TwitterDashboard.Rmd Untitled1.Rmd
Untitled22.Rmd VisualisationGraphsPlots.Rmd WebScrapping.Rmd
WhereToLearnR.Rmd

-----

# Getting Data into R / Veriyi R’a yükleme

<https://sbalci.github.io/MyRCodesForDataAnalysis/GettingDataVeriYukleme.nb.html>

  - Import Data
      - Import using RStudio
      - Import CSV File
      - Import TXT File
      - Import Excel File
          - Import Sheets
      - Import SPSS File
  - Export Data
      - Export to SPSS, while keeping labels

# Prepare Data for Analysis / Veriyi Analiz için hazırlamak

<https://sbalci.github.io/MyRCodesForDataAnalysis/PrepareData.nb.html>

## data.table

<https://sbalci.github.io/MyRCodesForDataAnalysis/datatable.nb.html>

# File organization best practices

<https://sbalci.github.io/MyRCodesForDataAnalysis/FileOrganization.nb.html>

# Analysis

## Descriptive Statistics, Exploratory Data Analysis, Summary Statistics

<https://sbalci.github.io/MyRCodesForDataAnalysis/DescriptiveStatistics.nb.html>

<https://sbalci.github.io/MyRCodesForDataAnalysis/ExplatoryDataAnalysisSummaryStatistics.nb.html>

<https://sbalci.github.io/MyRCodesForDataAnalysis/freq-tables.html>

the-lesser-known-stars-of-the-tidyverse.nb.html

## Hypothesis Testing

<https://sbalci.github.io/MyRCodesForDataAnalysis/HypothesisTesting.nb.html>

### Compare Means

<https://sbalci.github.io/MyRCodesForDataAnalysis/CompareMeans.nb.html>

### Compare Proportions

<https://sbalci.github.io/MyRCodesForDataAnalysis/CompareProportions.nb.html>

## Survival Analysis in R

<https://sbalci.github.io/MyRCodesForDataAnalysis/SurvivalAnalysis.nb.html>

<https://www.emilyzabor.com/tutorials/survival_analysis_in_r_tutorial.html>

## Contingency Tables

<https://sbalci.github.io/MyRCodesForDataAnalysis/ContingencyTables.nb.html>

## Other Analysis

### Regression

<https://sbalci.github.io/MyRCodesForDataAnalysis/Regression.nb.html>

### LinearRegression.nb.html

<https://sbalci.github.io/MyRCodesForDataAnalysis/LinearRegression.nb.html>

### General Linear Models

<https://sbalci.github.io/MyRCodesForDataAnalysis/GeneralLinearModels.nb.html>

### Decision Trees

<https://sbalci.github.io/MyRCodesForDataAnalysis/DecisionTreeKararAgaci.nb.html>

### Clustering

### K Means Clustering

<https://sbalci.github.io/MyRCodesForDataAnalysis/KMeansClustering.nb.html>

### Hierarchical Clustering

<https://sbalci.github.io/MyRCodesForDataAnalysis/HierarchicalClustering.nb.html>

# Graphs Plots

<https://sbalci.github.io/MyRCodesForDataAnalysis/VisualisationGraphsPlots.nb.html>

<https://sbalci.github.io/MyRCodesForDataAnalysis/Graphs.nb.html>

## Sankey Diagrams

<https://sbalci.github.io/MyRCodesForDataAnalysis/SankeyDiagrams.nb.html>

# Reporting

## Reproducible Research

<https://sbalci.github.io/MyRCodesForDataAnalysis/ReproducibleResearch.nb.html>

## Tables

<https://sbalci.github.io/MyRCodesForDataAnalysis/Table.nb.html>

<https://sbalci.github.io/MyRCodesForDataAnalysis/finalfit.nb.html>

<https://sbalci.github.io/MyRCodesForDataAnalysis/formattable.nb.html>

## Autoreport

<https://sbalci.github.io/MyRCodesForDataAnalysis/Autoreport.nb.html>

## shiny

<https://sbalci.github.io/MyRCodesForDataAnalysis/shiny.nb.html>

## Creating websites in R

<https://www.emilyzabor.com/tutorials/rmarkdown_websites_tutorial.html>

# Bioinformatics

## bioconductor

<https://sbalci.github.io/MyRCodesForDataAnalysis/bioconductor.nb.html>

<https://sbalci.github.io/MyRCodesForDataAnalysis/CancerInSilico.nb.html>

<https://sbalci.github.io/MyRCodesForDataAnalysis/CancerPackages.nb.html>

# Backup Analysis and Data

## GitHub

<https://sbalci.github.io/MyRCodesForDataAnalysis/GitHub.nb.html>

SyncingGitHubFork.nb.html

# Text Analysis Sentiment Analysis

<https://sbalci.github.io/MyRCodesForDataAnalysis/TextMining.nb.html>

## Twitter Analysis With R

<https://sbalci.github.io/MyRCodesForDataAnalysis/Twitter.nb.html>

## News

<https://sbalci.github.io/MyRCodesForDataAnalysis/news.nb.html>

## web scrapping

<https://sbalci.github.io/MyRCodesForDataAnalysis/WebScrapping.nb.html>

# Bibliography

Other Bibliographic Studies:
<https://sbalci.github.io/ResearchOnBibliography/>

<https://sbalci.github.io/MyRCodesForDataAnalysis/Bibliography.nb.html>

## PubMed

### RISmed

<https://sbalci.github.io/MyRCodesForDataAnalysis/RISmed.nb.html>

## ORCID

### rorcid

<https://sbalci.github.io/MyRCodesForDataAnalysis/rorcid.nb.html>

## Google Scholar

<https://sbalci.github.io/MyRCodesForDataAnalysis/GoogleScholar.nb.html>

### Scholar

### Coauthor

## Power Analysis

<https://sbalci.github.io/MyRCodesForDataAnalysis/PowerAnalysis.nb.html>

<https://sbalci.github.io/MyRCodesForDataAnalysis/Power_Analysis.nb.html>
<https://sbalci.github.io/MyRCodesForDataAnalysis/PowerAnalysis.nb.html>

## Formulas

<https://sbalci.github.io/MyRCodesForDataAnalysis/Formulas.nb.html>

## Flipping Coin

<https://sbalci.github.io/MyRCodesForDataAnalysis/FlippingCoin.nb.html>

# General Resources

<https://sbalci.github.io/MyRCodesForDataAnalysis/GeneralResources.nb.html>

<https://sbalci.github.io/MyRCodesForDataAnalysis/DataScienceLiveBook.nb.html>

# Package List

<https://sbalci.github.io/MyRCodesForDataAnalysis/RPackagesUsed.nb.html>

# Data List

<https://sbalci.github.io/MyRCodesForDataAnalysis/DataList.nb.html>

<https://sbalci.github.io/MyRCodesForDataAnalysis/eurostat.nb.html>

# Data Tools

<https://sbalci.github.io/MyRCodesForDataAnalysis/DataTools.nb.html>

# Miscellaneous

<https://sbalci.github.io/MyRCodesForDataAnalysis/codes.nb.html>

<https://sbalci.github.io/MyRCodesForDataAnalysis/OpenCPU.nb.html>

<https://sbalci.github.io/MyRCodesForDataAnalysis/papeR.nb.html>

<https://sbalci.github.io/MyRCodesForDataAnalysis/Tutorials.nb.html>

<https://sbalci.github.io/MyRCodesForDataAnalysis/PythonPandas.nb.html>

<https://sbalci.github.io/MyRCodesForDataAnalysis/lessR.nb.html>

<https://sbalci.github.io/MyRCodesForDataAnalysis/arsenal.nb.html>

<https://sbalci.github.io/MyRCodesForDataAnalysis/rchess.nb.html>

<https://sbalci.github.io/MyRCodesForDataAnalysis/EvidenceSynthesisProjects.nb.html>

<https://sbalci.github.io/MyRCodesForDataAnalysis/MachineLearning.nb.html>

<https://sbalci.github.io/MyRCodesForDataAnalysis/Correlations.nb.html>

<https://xgboost.readthedocs.io/en/latest/index.html>

<https://sbalci.github.io/MyRCodesForDataAnalysis/R-Tipps.nb.html>

# Feedback

  - [Yours truly](https://github.com/sbalci) would like to hear your
    feedback: *[feedback form](https://goo.gl/forms/YjGZ5DHgtPlR1RnB3)*

  - See <https://sbalci.github.io/> for other analysis.

You may also contact with me with the comment field below.

-----

{% if page.comments %}

<script id="dsq-count-scr" src="//https-sbalci-github-io.disqus.com/count.js" async></script>

<div id="disqus_thread">

</div>

<script>

/**
*  RECOMMENDED CONFIGURATION VARIABLES: EDIT AND UNCOMMENT THE SECTION BELOW TO INSERT DYNAMIC VALUES FROM YOUR PLATFORM OR CMS.
*  LEARN WHY DEFINING THESE VARIABLES IS IMPORTANT: https://disqus.com/admin/universalcode/#configuration-variables*/
/*
var disqus_config = function () {
this.page.url = PAGE_URL;  // Replace PAGE_URL with your page's canonical URL variable
this.page.identifier = PAGE_IDENTIFIER; // Replace PAGE_IDENTIFIER with your page's unique identifier variable
};
*/
(function() { // DON'T EDIT BELOW THIS LINE
var d = document, s = d.createElement('script');
s.src = 'https://https-sbalci-github-io.disqus.com/embed.js';
s.setAttribute('data-timestamp', +new Date());
(d.head || d.body).appendChild(s);
})();
</script>

<noscript>

Please enable JavaScript to view the
<a href="https://disqus.com/?ref_noscript">comments powered by
Disqus.</a>

</noscript>

{% endif %}

-----



