---
title: "My R Codes For Data Analysis"
subtitle: "In this repository I am going to collect `R codes` for data analysis. Codes are from various resources and I try to give original link as much as possible."
author: "[Serdar Balcı, MD, Pathologist](https://www.serdarbalci.com/)"
date: '`r format(Sys.Date())`'
output: 
  html_notebook: 
    fig_caption: yes
    highlight: tango
    number_sections: yes
    theme: paper
    toc: yes
    toc_depth: 5
    toc_float: yes
  html_document: 
    code_folding: hide
    df_print: kable
    keep_md: yes
    number_sections: yes
    theme: cerulean
    toc: yes
    toc_float: yes
    highlight: kate
---


# Prepare Data for Analysis / Veriyi Analiz için hazırlamak

## The Quartz guide to bad data

>    An exhaustive reference to problems seen in real-world data along with suggestions on how to resolve them.

https://github.com/Quartz/bad-data-guide


## Kötü veri kılavuzu

Kötü veri kılavuzu

https://sbalci.github.io/Kotu-Veri-Kilavuzu/index.html

## data organization organizing data in spreadsheets

https://kbroman.org/dataorg/

Daniel Kaplan. (2018) Teaching Stats for Data Science. The American Statistician 72:1, pages 89-96. 

https://doi.org/10.1080/00031305.2017.1375989


## Tidy Data

Hadley Wickham.
Tidy data.
The Journal of Statistical Software, vol. 59, 2014.

http://vita.had.co.nz/papers/tidy-data.html
https://www.jstatsoft.org/article/view/v059i10
http://dx.doi.org/10.18637/jss.v059.i10


### Keep SPSS labels

```{r}
library(foreign) # foreign paketi yükleniyor
```

read.spss komutu ile değer etiketlerini almasını ve bunu liste olarak değil de data.frame olarak kaydetmesini istiyoruz

```{r}
mydata <- read.spss("mydata.sav", use.value.labels = TRUE, to.data.frame = TRUE)
```

aktardığımız data.frame'in özellikleri (attr) içinde değişkenlerin etiketleri var, bunları dışarı çıkartıyoruz

```{r}
VariableLabels <- as.data.frame(attr(mydata, "variable.labels"))
```


elde ettiğimiz data.frame'deki satır isimleri değişkenlerin isimleri oluyor, karşılarında da değişken etiketleri var
satır isimlerini de dışarı çıkartıyoruz

```{r}
VariableLabels$original <- rownames(VariableLabels)
```

Değişken etiketi olanları etiketleri ile diğerlerini olduğu gibi saklıyoruz  

```{r}
VariableLabels$label[VariableLabels$label ==""] <- NA 
VariableLabels$colname <- VariableLabels$original
VariableLabels$colname[!is.na(VariableLabels$label)] <- as.vector(VariableLabels$label[!is.na(VariableLabels$label)])
```

son olarak da data.frame'deki sütun isimlerini değiştiriyoruz

```{r}
names(mydata) <- VariableLabels$colname
```


### Make both computer and human readible variable names

turkce karakter donusumu

```{r turkce karakter donusumu}
# https://suatatan.wordpress.com/2017/10/07/bulk-replacing-turkish-characters-in-r/

to.plain <- function(s) {
        # 1 character substitutions
    old1 <- "çğşıüöÇĞŞİÖÜ"
    new1 <- "cgsiuocgsiou"
    s1 <- chartr(old1, new1, s)
    # 2 character substitutions
    old2 <- c("œ", "ß", "æ", "ø")
    new2 <- c("oe", "ss", "ae", "oe")
    s2 <- s1
    for(i in seq_along(old2)) s2 <- gsub(old2[i], new2[i], s2, fixed = TRUE)
    s2
}

names(df) <- make.names(to.plain(tolower(names(df))))

names(df) <- names(df) %>% 
    tolower() %>% 
    to.plain() %>% 
    make.names()

df$source=as.vector(sapply(df$source,to.plain))

make.names(tolower(names(df)))
to.plain(names(df))

purrr::map(df, to.plain)

```

### Anonimisation

### Add subject ID to the data / veriye ID ekleme

```{r}
df <- tibble::rowid_to_column(df, "subject")
```





## Data reorganization

```{r}
scabies <- read.csv(file = "http://datacompass.lshtm.ac.uk/607/2/S1-Dataset_CSV.csv", header = TRUE, sep = ",")

scabies$gender == "male"

scabies$age[scabies$gender == "male"]

mean(scabies$age[scabies$gender == "male"])


scabies %>% 
    filter(gender == "male") %>% 
    summarise_at("age" ,mean) 


```



```{r}

scabies$agegroups <- as.factor(cut(scabies$age, c(0,10,20,Inf), labels = c("0-10","11-20","21+"), include.lowest = TRUE)) 

scabies$house_cat <- as.factor(cut(scabies$house_inhabitants, c(0,5,10,Inf), labels = c("0-5","6-10","10+"), include.lowest = TRUE))


table(scabies$house_cat, scabies$house_inhabitants)

```

```{r}
ebola$status <- as.numeric(ebola$status) 

```


```{r}
ebola$transmission <- recode(ebola$transmission, syringe = "needle")

```

```{r}
scabies$house_cat <- relevel(scabies$house_cat, ref = "0-5")
#Make 0-5 household size the baseline group
```





```{r}
df <- data.frame(month=rep(1:3,2),
                 student=rep(c("Amy", "Bob"), each=3),
                 A=c(9, 7, 6, 8, 6, 9),
                 B=c(6, 7, 8, 5, 6, 7))
#Here we have a where each student is on a different row for each month
#The students took two tests A and B. 
#For each student/month combination we have a value for A and a value for B

df2 <- gather(df,test,score,A:B)
#Make a new datatable df2
#Have a column called "test". 
#This will have the value either A or B as these are the names of the columns we specified.
#Have a column called "score". 
#This will have the value previously in column A or B respectively for each row

df2
```


```{r}
#Now we have a single row for each combination of month/student/test 
#Their score is in the score column

df3 <- spread(df2,test,score)
#Make a new datatable df3
#Make a column for each unique value in the test variable.
#Name each of these columns based on that unique value
#Under each column put the corresponding value that was in the score column

df3
```

```{r}
dt3 <- expandRows(dt, 2)
#Expand the original datatable. Replicate each row by the value in column 2. 
dt3
```










































<!-- # gerekli paketi yükleme -->
<!-- library(tidyverse) -->
<!-- library(haven) -->
<!-- # dosyayı yükleme -->
<!-- EDT256 <- read_sav("EDT256.sav") -->



<!-- # gerekli sütunları seçme -->
<!-- EDT256 <- EDT256 %>% -->
<!--     select(subject, tanı, starts_with("beck")) -->

<!-- # değişken değerlerini yeniden atama -->
<!-- EDT256$tanı <- as_factor(EDT256$tanı, labels = "values") -->

<!-- # yatay veriyi uzun hale getirme -->
<!-- EDT256_new <- EDT256 %>% -->
<!--     gather(- c("subject","tanı"), key = zaman, value = beck_int_score) -->


<!-- # değişkenleri rakamsal hale getirme -->
<!-- EDT256_new$zaman[which(EDT256_new$zaman == "beck_int_P")] <- 0 -->
<!-- EDT256_new$zaman[which(EDT256_new$zaman == "beck_int_A1")] <- 1 -->
<!-- EDT256_new$zaman[which(EDT256_new$zaman == "beck_int_A2")] <- 2 -->

<!-- # değişken değerlerini atama  -->
<!-- EDT256_new$zaman <- factor(EDT256_new$zaman, levels = c(0,1,2), -->
<!--                            labels = c("Tedavi Öncesi", "T. Sonrası 1. Hafta", -->
<!--                                       "T. Sonrası 2. Hafta")) -->


<!-- # nparLD analizi -->

<!-- # gerekli paketi yükleme -->
<!-- library(nparLD) -->

<!-- # model oluşturma -->
<!-- modelEDT256 <- nparLD(beck_int_score ~ tanı * zaman, data = EDT256_new, -->
<!--                       subject = "subject", -->
<!--                       plot.CI = TRUE, show.covariance = TRUE) -->

<!-- # model sonucunu yazdır -->
<!-- out <- capture.output(modelEDT256) -->
<!-- cat("EDT256 Model", out, file = "EDT256.txt", sep = "\n", append=TRUE) -->

<!-- # model grafiği -->
<!-- plot(modelEDT256) -->

<!-- # plot sonucunu yazdır -->
<!-- out2 <- capture.output(plot(modelEDT256)) -->
<!-- cat("\n","EDT256 Plot", out2, file = "EDT256.txt", sep = "\n", append = TRUE) -->

<!-- # grafiği yazdır -->
<!-- jpeg('modelEDT256.jpeg') -->
<!-- plot(modelEDT256) -->
<!-- dev.off() -->

<!-- # model özeti -->
<!-- summary(modelEDT256) -->

<!-- # model özeti sonucunu yazdır -->
<!-- out3 <- capture.output(modelEDT256) -->
<!-- cat("\n","EDT256 summary", out3, file = "EDT256.txt", sep = "\n", append=TRUE) -->


<!-- # ek olarak boxplot oluşturma -->
<!-- boxplot(beck_int_score ~ tanı * zaman, data = EDT256_new, -->
<!--         names = FALSE,col = c("grey",2),lwd = 2) -->
<!-- axis(1,at = 1.5,labels = "Tedavi Öncesi",font = 2,cex = 3) -->
<!-- axis(1,at = 3.5,labels = "T. Sonrası 1. Hafta",font = 2,cex = 3) -->
<!-- axis(1,at = 5.5,labels = "T. Sonrası 2. Hafta",font = 2,cex = 3) -->
<!-- legend(5,35,c("Tanı 1","Tanı 2"), -->
<!--        lwd = c(2,2), -->
<!--        col = c("grey",2),cex = 0.7) -->

<!-- # boxplot yazdır -->
<!-- jpeg('boxplotEDT256.jpeg') -->
<!-- boxplot(beck_int_score ~ tanı * zaman, data = EDT256_new, -->
<!--         names = FALSE,col = c("grey",2),lwd = 2) -->
<!-- axis(1,at = 1.5,labels = "Tedavi Öncesi",font = 2,cex = 3) -->
<!-- axis(1,at = 3.5,labels = "T. Sonrası 1. Hafta",font = 2,cex = 3) -->
<!-- axis(1,at = 5.5,labels = "T. Sonrası 2. Hafta",font = 2,cex = 3) -->
<!-- legend(5,35,c("Tanı 1","Tanı 2"), -->
<!--        lwd = c(2,2), -->
<!--        col = c("grey",2),cex = 0.7) -->
<!-- dev.off() -->


https://stackoverflow.com/questions/22353633/filter-for-complete-cases-in-data-frame-using-dplyr-case-wise-deletion


df %>% na.omit
or this:

df %>% filter(complete.cases(.))
or this:

library(tidyr)
df %>% drop_na
If you want to filter based on one variable's missingness, use a conditional:

df %>% filter(!is.na(x1))
or

df %>% drop_na(x1)
Other answers indicate that of the solutions above na.omit is much slower but that has to be balanced against the fact that it returns and row indices of the omitted rows as the na.action attribute whereas the other solutions above do not.

str(df %>% na.omit)
'data.frame':   2 obs. of  2 variables:
$ x1: num  1 2
$ x2: num  1 2
- attr(*, "na.action")= 'omit' Named int  3 4
    ..- attr(*, "names")= chr  "3" "4"



ozp <- veri %>% 
    select(RaporNo, Hasta, cinsiyet, Yas,
           ozp_parca, ozp_kaset, ozp_cap, ozp_tani, ozp_kod) %>% 
    filter(!is.na(ozp_parca) | !is.na(ozp_kaset) | !is.na(ozp_cap) | !is.na(ozp_tani) | !is.na(ozp_kod)
    )

ozp2 <- veri %>% 
    select(RaporNo, Hasta, cinsiyet, Yas,
           ozp_parca, ozp_kaset, ozp_cap, ozp_tani, ozp_kod) %>% 
    filter(complete.cases(ozp_parca, ozp_kaset, ozp_cap, ozp_tani, ozp_kod)
    )

ozp3 <- veri %>% 
    select(RaporNo, Hasta, cinsiyet, Yas,
           ozp_parca, ozp_kaset, ozp_cap, ozp_tani, ozp_kod) %>% 
    na.omit(ozp_parca, ozp_kaset, ozp_cap, ozp_tani, ozp_kod)
    






