---
output:
  rmarkdown::html_vignette: 
    css: 
    - !expr system.file("rmarkdown/templates/html_vignette/resources/vignette.css", package = "rmarkdown")
vignette: >
  %\VignetteIndexEntry{Recommendations for Rmarkdown}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r summarytool options 1, include=FALSE}
library(knitr)
opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=TRUE, results='asis')
```


```{r summarytool options 2, echo=TRUE}
library(summarytools)
st_css()
```


```{r summarytool options 3}
st_options(bootstrap.css     = FALSE,       # Already part of the theme so no need for it
           plain.ascii       = FALSE,       # One of the essential settings
           style             = "rmarkdown", # Idem.
           dfSummary.silent  = TRUE,        # Suppresses messages about temporary files
           footnote          = NA,          # Keeping the results minimalistic
           subtitle.emphasis = FALSE)       # For the vignette theme, this gives
                                            # much better results. Your mileage may vary.
``` 



```{r summarytools freq Rmarkdown Style}
freq(tobacco$gender, style = 'rmarkdown')
```


## HTML Rendering
```{r eval=FALSE, include=FALSE, echo=TRUE}
print(freq(tobacco$gender), method = 'render')
```

If you find the table too large, you can use `table.classes = 'st-small'` - an 
example is provided further below.

--------------------------------------------------------------------------------

<a href="#top">Back to top</a>

# ctable() {#ctable}

## Rmarkdown Style

Tables with heading spanning over 2 rows are not fully supported in markdown 
(yet), but the result is getting close to acceptable. This, however, is not
true for all themes. That's why the rendering method is preferred.

```{r eval=FALSE, include=FALSE, echo=TRUE}
ctable(tobacco$gender, tobacco$smoker, style = 'rmarkdown')
```

## HTML Rendering

For best results, use this method.

```{r }
print(ctable(tobacco$gender, tobacco$smoker), method = 'render')
```

--------------------------------------------------------------------------------
 
<a href="#top">Back to top</a>
 
# descr() {#descr}
`descr()` is also best used with `style = 'rmarkdown'`, and HTML rendering is 
also supported.

## Rmarkdown Style
```{r eval=FALSE, include=FALSE, echo=TRUE}
descr(tobacco, style = 'rmarkdown')
```


## HTML Rendering

We'll use table.classes = 'st-small' to show how it affects the table's size
(compare to the `freq()` table rendered earlier).

```{r eval=FALSE, include=FALSE, echo=TRUE}
print(descr(tobacco), method = 'render', table.classes = 'st-small')
```
 
--------------------------------------------------------------------------------

<a href="#top">Back to top</a>

# dfSummary() {#dfsummary}

## Grid Style

This style gives good results, and since v0.9, the graphs are shown as true 
images. Don't forget to specify `plain.ascii = FALSE` (or set it as a global
option with `st_options(plain.ascii = FALSE)`), or you won't get good results.

```{r , eval=FALSE}
dfSummary(tobacco, style = 'grid', graph.magnif = 0.75, tmp.img.dir = "/tmp")
```




```{r eval=FALSE, include=FALSE, echo=TRUE}
print(dfSummary(tobacco, graph.magnif = 0.75), method = 'render')
```


