---
title: "R Packages Used"
output: html_notebook
---

<!-- ```{r setup, cache = F, warning = FALSE} -->

<!-- knitr::opts_chunk$set( -->
<!-- 	error = TRUE, -->
<!-- 	message = FALSE, -->
<!-- 	warning = FALSE, -->
<!-- 	eval = FALSE, -->
<!-- 	include = TRUE -->
<!-- ) -->
<!-- ``` -->



# ggstatsplot

ggplot2 Based Plots with Statistical Details

https://indrajeetpatil.github.io/ggstatsplot/


## ggcoefstats

https://indrajeetpatil.github.io/ggstatsplot/articles/ggcoefstats.html

# Choroplethr

https://arilamstein.com/open-source/



# purrr

https://colinfay.me/happy-dev-purrr/

# knitcitations

http://www.carlboettiger.info/2012/05/30/knitcitations.html

# infer
Tidy Statistical Inference
https://cran.r-project.org/web/packages/infer/index.html

https://kbroman.org/pkg_primer/

## Packages to be studied


```{r}
packagefinder::findPackage(c("pubmed", "bibliography"))
```

https://cran.rstudio.com/web/packages/sys/

# scales

Scale Functions for Visualization

https://cran.r-project.org/web/packages/scales/index.html

```{r}
paste0(round(.20394*100, 1), "%")
scales::percent(.20394)
```


# animation
A Gallery of Animations in Statistics and Utilities to Create Animations
https://cran.r-project.org/web/packages/animation/

# gganimate
A Grammar of Animated Graphics
https://github.com/thomasp85/gganimate


https://cran.r-project.org/web/packages/naniar/index.html

https://hughjonesd.github.io/anim.plots/anim.plots.html

You Can Design a Good Chart with R
https://towardsdatascience.com/you-can-design-a-good-chart-with-r-5d00ed7dd18e

Bubble-grid-maps
https://jschoeley.github.io/2018/06/30/bubble-grid-map.html

Taking control of animations in R and demystifying them in the process 
https://www.data-imaginist.com/2017/animating-the-logo/?utm_content=bufferd418f&utm_medium=social&utm_source=twitter.com&utm_campaign=buffer
 
https://cran.r-project.org/web/packages/rticles/rticles.pdf



https://colinfay.me/build-api-wrapper-package-r/

https://www.datacamp.com/community/tutorials/setup-data-science-environment

https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html####installation

https://cran.r-project.org/web/packages/expss/vignettes/tables-with-labels.html

https://cran.r-project.org/web/packages/tabulizer/vignettes/tabulizer.html

https://github.com/benjaminrich/table1

https://cran.r-project.org/web/packages/tableone/vignettes/introduction.html

https://twitter.com/mitchoharawild/status/1007297976711110659?s=12

https://twitter.com/mf_viz/status/1004954297962917891?s=12

https://github.com/cmap/morpheus.R

https://github.com/talgalili/heatmaply/

https://github.com/rstudio/d3heatmap

http://worksmarter.pl/en/post/webscraping-case-study-1/

http://worksmarter.pl/en/post/job-automation-r-1/

http://www.brodrigues.co/blog/2018-06-10-scraping_pdfs/

https://www.r-bloggers.com/how-to-plot-with-ggiraph/

https://www.r-bloggers.com/understanding-pca-using-stack-overflow-data/

https://www.r-bloggers.com/beautiful-and-powerful-correlation-tables-in-r/

http://journals.plos.org/plosone/article?id=10.1371%2Fjournal.pone.0188299

https://github.com/trinker/reports

Animated Directional Chord Diagrams
https://guyabel.com/post/animated-directional-chord-diagrams/


modelDown: a website generator for your predictive models
http://smarterpoland.pl/index.php/2018/06/modeldown-a-website-generator-for-your-predictive-models/

# drake
https://ropensci.github.io/drake/


## chromoMap

An R package for Interactive visualization and mapping of human chromosomes

https://cran.r-project.org/web/packages/chromoMap/vignettes/chromoMap.html

## tabplot

Tableplot, a Visualization of Large Datasets

https://cran.r-project.org/web/packages/tabplot/index.html

https://cran.r-project.org/web/packages/tabplot/vignettes/tabplot-vignette.html

https://cran.r-project.org/web/packages/tabplot/vignettes/tabplot-timings.html

## treemap

Treemap Visualization

https://cran.r-project.org/web/packages/treemap/index.html

## VIM

Visualization and Imputation of Missing Values

https://cran.r-project.org/web/packages/VIM/index.html

## survey

https://cran.r-project.org/web/packages/survey/index.html

## tidytext

https://cran.r-project.org/web/packages/tidytext/index.html

https://cran.r-project.org/web/packages/tidytext/vignettes/tf_idf.html

https://cran.r-project.org/web/packages/tidytext/vignettes/tidying_casting.html

https://cran.r-project.org/web/packages/tidytext/vignettes/tidytext.html

https://cran.r-project.org/web/packages/tidytext/vignettes/topic_modeling.html


## rapport  an R templating system

http://rapport-package.info/

## ztable

https://github.com/cardiomoon/ztable

## texreg

https://cran.r-project.org/web/packages/texreg/vignettes/texreg.pdf

## SortableHTMLTables

https://cran.r-project.org/web/packages/SortableHTMLTables/index.html

## hwriter

https://cran.r-project.org/web/packages/hwriter/vignettes/hwriter.pdf

## HTMLUtils

https://cran.r-project.org/web/packages/HTMLUtils/index.html

## htmlTable
https://cran.r-project.org/web/packages/htmlTable/index.html

## formattable

https://cran.r-project.org/web/packages/formattable/index.html

## DT

DT: An R interface to the DataTables library

https://rstudio.github.io/DT/

## stargazer

Well-Formatted Regression and Summary Statistics Tables

https://cran.r-project.org/web/packages/stargazer/index.html




## conflicted

## psycho

```{r, eval=FALSE, include=TRUE}
install.packages("devtools")
library("devtools")
install_github("neuropsychology/psycho.R")
library("psycho")
```


## styler

## tidyverse

## splitstackshape

- The “splitstackshape” package for R

https://www.r-bloggers.com/the-splitstackshape-package-for-r/

## epiR

Basic Epi

install.packages("epiR")

## lmtest

Some useful epitools especially 2*2 tables and stratified MH Odds

install.packages("lmtest")

## popEpi

install.packages("popEpi")

## Extra tools to go with 'Epi' and make nice rate tables

## survival

install.packages("survival")

for survial analysis, kaplan-meier plots and cox regression

## survminer

install.packages("survminer")

Really nice KM plots!

## Random-Effects Modeks

install.packages("lme4")

install.packages("sjstats")


## Multiple Imputation

install.packages("mice")


install.packages("arsenal")

## Really nice summmary tables

## Complex survey data analysis

install.packages("survey")

## For handling complex survey data

install.packages("ICC")


## Alternative methods for ICC calculation from survey data

## Meta-analysis

install.packages("meta")


install.packages("metafor")


install.packages("workflowr")


install.packages("DiagrammeR")


install.packages("tangram")


devtools::install_github("lbusett/insert_table")


```{r}
#### Obtain names of all packages on CRAN
names.available.packages <- rownames(available.packages())

#### Extract packages names that contain Rcmdr
Rcmdr.related.packages <- names.available.packages[grep("Rcmdr", names.available.packages)]
Rcmdr.related.packages

#### Install these packages
install.packages(pkgs = Rcmdr.related.packages)
```



```{r}
usePackage <- function(p) {
  if (!is.element(p, installed.packages()[, 1])) {
    install.packages(p, dep = TRUE)
  }
  require(p, character.only = TRUE)
}
```



```{r}
file.edit("~/Desktop/foo/.Rprofile")
## This opens up a script window, within which you can enter in your library commands
library(ggplot2)
library(scales)
library(plyr)
library(reshape2)
```






## abind



## acepack



## AlgDesign



## AnnotationDbi



## aplpack



## arm



## assertthat



## backports



## base



## base64enc



## BCA



## BH



## BiasedUrn



## bindr



## bindrcpp



## Biobase



## BiocGenerics



## BiocInstaller



## bit



## bit64



## bitops



## blob



## boot



## broom



## BsMD



## ca



## car



## caTools



## cellranger



## checkmate



## class



## cluster



## clv



## coda



## codetools



## coin



## colorspace



## combinat



## compiler



## conf.design



## curl



## data.table



## datasets



## date



## DBI



## deldir



## depthTools



## DiceDesign



## dichromat



## digest



## DoE.base



## DoE.wrapper



## doParallel



## dplyr



## e1071



## effects



## ENmisc



## epiR



## estimability



## evaluate



## ez



## flexclust



## forcats



## foreach



## foreign



## formatR



## Formula



## fracdiff



## FrF2



## gdata



## ggplot2

http://www.cookbook-r.com/Graphs/

### ggplot2 extensions

http://www.ggplot2-exts.org/gallery/

http://corybrunson.github.io/ggalluvial/

http://www.sthda.com/english/rpkgs/survminer/

## ggthemes



## ggvis



## glue



## goftest



## graphics



## grDevices



## grid



## gridBase



## gridExtra



## gtable



## gtools



## haven



## highr



## Hmisc



## hms



## htmlTable



## htmltools



## htmlwidgets



## httpuv



## httr



## igraph



## IRanges



## irlba



## iterators



## jsonlite



## KernSmooth



## knitr



## labeling



## lattice



## latticeExtra



## lazyeval



## leaps



## lhs



## lme4



## lmtest



## lsmeans



## lubridate



## magrittr



## markdown



## MASS



## Matrix



## matrixcalc



## MatrixModels



## memoise



## methods



## mgcv



## mi



## mime



## minqa



## mnormt



## modelr



## modeltools



## multcomp



## munsell



## mvtnorm



## nlme



## nloptr



## NLP



## NMF



## nnet



## nortest



## openssl



## ordinal



## orloca



## orloca.es



## parallel



## pbkrtest



## pkgconfig



## pkgmaker



## plogr



## plyr



## polyclip



## psych



## purrr

https://colinfay.me/happy-dev-purrr/

## quadprog



## quantmod



## quantreg



## R2HTML



## R6



## randtests



## Rcmdr



## RcmdrMisc



## RcmdrPlugin.BCA



## RcmdrPlugin.coin



## RcmdrPlugin.depthTools



## RcmdrPlugin.DoE



## RcmdrPlugin.doex



## RcmdrPlugin.EACSPIR



## RcmdrPlugin.EBM



## RcmdrPlugin.epack



## RcmdrPlugin.EZR



## RcmdrPlugin.KMggplot2



## RcmdrPlugin.mosaic



## RcmdrPlugin.MPAStats



## RcmdrPlugin.orloca



## RcmdrPlugin.plotByGroup



## RcmdrPlugin.qual



## RcmdrPlugin.SCDA

## RcmdrPlugin.sampling

Tools for sampling in Official Statistical Surveys

https://cran.r-project.org/web/packages/RcmdrPlugin.sampling/index.html


## RcmdrPlugin.seeg



## RcmdrPlugin.SLC



## RcmdrPlugin.SM



## RcmdrPlugin.steepness



## RcmdrPlugin.survival



## RcmdrPlugin.TeachingDemos



## RcmdrPlugin.temis



## RcmdrPlugin.UCA



## RColorBrewer



## Rcpp



## RcppArmadillo



## RcppEigen



## readr



## readxl



## registry



## relimp



## rematch



## reshape



## reshape2



## rgl



## RISmed



## rJava



## rlang



## rmarkdown



## RMySQL



## rngtools



## rpart



## rpart.plot



## rprojroot



## rsm



## RSQLite



## rvest



## S4Vectors



## sandwich



## scales



## scatterplot3d



## SCMA



## SCRT



## SCVA



## seeg



## selectr



## sem



## sfsmisc



## sgeostat



## shiny



## shinythemes



## slam



## SLC



## sourcetools



## SparseM



## spatial



## spatstat



## spatstat.utils



## splines



## stats



## stats4



## steepness



## stringi



## stringr



## survival



## tcltk



## tcltk2



## TeachingDemos



## tensor



## TH.data



## tibble



## tidyr



## tidyverse



## timeDate



## tkrplot



## tm



## tools



## tseries



## TTR



## ucminf



## utils



## vcd



## viridis



## viridisLite



## XLConnect



## XLConnectJars



## xml2



## xtable



## xts



## yaml



## zoo















install.packages("stargazer")

install.packages("pander")

install.packages("tables")

install.packages("ascii")

install.packages("xtable")

devtools::install_github("hadley/dplyr")


install.packages("gapminder")

install.packages("alluvial")


vignette("databases", package = "dplyr")

install.packages("robustbase")

install.packages("insuranceData")

install.packages("Lahman")


install.packages("tidyverse")

install.packages("qdap")

install.packages("openxlsx")


devtools::install_github("kassambara/r2excel")

install.packages("WriteXLS")

install.packages("XLConnect")

library(XLConnect)


```{r}
if (!require(wordcloud)) {
  install.packages("wordcloud")
  library(wordcloud)
}
```



```{r}
installed <- as.data.frame(installed.packages())
write.csv(installed, "installed_previously.csv")

installedPreviously <- read.csv("installed_previously.csv")
baseR <- as.data.frame(installed.packages())
toInstall <- setdiff(installedPreviously, baseR)

install.packages(toInstall)


packagelist <- installed.packages()
class(packagelist)
packagelist[, 1]
```




## Rcmdr

```{r}
install.packages("Rcmdr")
install.packages("RcmdrPlugin.BCA")
install.packages("RcmdrPlugin.coin")
install.packages("RcmdrPlugin.depthTools")
install.packages("RcmdrPlugin.doBy")
install.packages("RcmdrPlugin.DoE")
install.packages("RcmdrPlugin.doex")
install.packages("RcmdrPlugin.EACSPIR")
install.packages("RcmdrPlugin.EBM")
install.packages("RcmdrPlugin.epack")
install.packages("RcmdrPlugin.EZR")
install.packages("RcmdrPlugin.HH")
install.packages("RcmdrPlugin.IPSUR")
install.packages("RcmdrPlugin.KMggplot2")
install.packages("RcmdrPlugin.mosaic")
install.packages("RcmdrPlugin.MPAStats")
install.packages("RcmdrPlugin.orloca")
install.packages("RcmdrPlugin.plotByGroup")
install.packages("RcmdrPlugin.qcc")
install.packages("RcmdrPlugin.qual")
install.packages("RcmdrPlugin.SCDA")
install.packages("RcmdrPlugin.seeg")
install.packages("RcmdrPlugin.SLC")
install.packages("RcmdrPlugin.SM")
install.packages("RcmdrPlugin.StatisticalURV")
install.packages("RcmdrPlugin.steepness")
install.packages("RcmdrPlugin.survival")
install.packages("RcmdrPlugin.TeachingDemos")
install.packages("RcmdrPlugin.temis")
install.packages("RcmdrPlugin.UCA")
```


```{r}
source("https://bioconductor.org/biocLite.R")
biocLite()
```


install.packages("tidyverse")

install.packages("devtools")

devtools::install_github("hadley/colformat")

devtools::install_github("ropenscilabs/skimr")

install.packages("hflights")

install.packages("dbplyr")

install.packages("xlsx")

require(devtools)

install_github("ProjectMOSAIC/mosaic")

install.packages("jmv")


install.packages("wordcloud")

install.packages("https://cran.r-project.org/src/contrib/Archive/tm/tm_0.6.tar.gz", repos = NULL)

install.packages("SnowballC")

install.packages("RColorBrewer")

install.packages("tidytext")

install.packages("packrat")

install.packages("testthat")

install.packages("prettydoc")

install.packages("rmdformats")

install.packages(c("fivethirtyeight", "tidyverse", "knitr", "kableExtra", "ggthemes"))

library(devtools)

install_github("SPSStoR", username = "lebebr01")

library(SPSStoR)


```{r}
ip <- installed.packages()
pkgs.to.remove <- ip[!(ip[, "Priority"] %in% c("base", "recommended")), 1]
sapply(pkgs.to.remove, remove.packages)
sapply(pkgs.to.remove, install.packages)
```




```{r}
install.packages("devtools")
devtools::install_github("AndreaCirilloAC/updateR")
library(updateR)
updateR(admin_password = "") ## Where "PASSWORD" stands for your system password

```






survival

survminer

install.packages("tutorial")


devtools::install_github("romainfrancois/highlight")

install.packages("highr", repos = "http://rforge.net", type = "source")



install.packages("xplain")





```{r remove all user installed packages in R, eval=FALSE, include=TRUE}
## How to remove all user installed packages in R
## https://www.r-bloggers.com/how-to-remove-all-user-installed-packages-in-r/

## create a list of all installed packages
ip <- as.data.frame(installed.packages())
head(ip)
## if you use MRO, make sure that no packages in this library will be removed
ip <- subset(ip, !grepl("MRO", ip$LibPath))
## we don't want to remove base or recommended packages either\
ip <- ip[!(ip[,"Priority"] %in% c("base", "recommended")),]
## determine the library where the packages are installed
path.lib <- unique(ip$LibPath)
## create a vector with all the names of the packages you want to remove
pkgs.to.remove <- ip[,1]
head(pkgs.to.remove)
## remove the packages
sapply(pkgs.to.remove, remove.packages, lib = path.lib)
```


## Schedule R Script

library(knitr)

library(markdown)
 

knit("SchedulePubMedAnalysis.Rmd")

markdownToHTML("SchedulePubMedAnalysis.md", "docs/SchedulePubMedAnalysis.html")

setwd("~")

file.choose()

library(rmarkdown)


Preperation Packages Schedule R Script

 https://github.com/jkeirstead/scholar

 http://rogiersbart.blogspot.com.tr/2015/05/put-google-scholar-citations-on-your.html

 http://tuxette.nathalievilla.org/?p=1682

 https://github.com/sunitj/scholar

 https://tgmstat.wordpress.com/2013/09/11/schedule-rscript-with-cron/

 https://github.com/ropensci/git2r
     

 library(knitr)

 library(markdown)
 
 install.packages('data.table')

 install.packages('knitr')

 install.packages('miniUI')

 install.packages('shiny')

 install.packages('shinyFiles')
 
 install.packages("taskscheduleR", repos = "http://www.datatailor.be/rcube", type = "source")
 
 devtools::install_github("bnosac/cronR")

 install.packages('scholar')
 
 
 install.packages("git2r")


## flatxml

http://www.zuckarelli.de/flatxml/articles/example/example.html

```{r}
xmldata <- flatxml::fxml_importXMLFlat("data/PathologyTurkey.xml")

```


## roomba

General purpose API response tidier

https://github.com/ropenscilabs/roomba/

```{r}
roomba::shiny_roomba()
```



## tufterhandout

Tufte-style html document format for rmarkdown

https://cran.r-project.org/web/packages/tufterhandout/index.html

```{r}
## install.packages("tufterhandout")
library(tufterhandout)
```

## papeR

[https://sbalci.github.io/MyRCodesForDataAnalysis/papeR.nb.html](https://sbalci.github.io/MyRCodesForDataAnalysis/papeR.nb.html)

## tm

install.packages("tm")

https://cran.r-project.org/web/packages/tm/vignettes/tm.pdf

---

https://atom.io/packages/hydrogen


---

R Package Documentation
https://rdrr.io/
R Packages Search and Statistics
https://www.rpackages.io/
ReporteRs is an R package for creating Microsoft Word and Powerpoint documents.
https://davidgohel.github.io/ReporteRs/
officer Manipulation of Microsoft Word and PowerPoint Documents
https://cran.r-project.org/web/packages/officer/
pubh
https://cran.rstudio.com/web/packages/pubh/vignettes/introduction.html
What does visdat do?
Initially inspired by csv-fingerprint, vis_dat helps you visualise a dataframe and “get a look at the data” by displaying the variable classes in a dataframe as a plot with vis_dat, and getting a brief look into missing data patterns using vis_miss.
https://www.tidyverse.org/
https://cran.r-project.org/web/packages/shiny/index.html
https://rmarkdown.rstudio.com/
http://ggplot2.org/
https://yihui.name/knitr/
http://vita.had.co.nz/papers/tidy-data.html
https://blog.rstudio.com/2015/04/09/readr-0-1-0/
http://readxl.tidyverse.org/
https://cran.r-project.org/web/packages/lubridate/vignettes/lubridate.html
https://github.com/r-lib/devtools
https://cran.r-project.org/web/packages/magrittr/index.html
http://rstudio.github.io/packrat/
https://cran.r-project.org/web/packages/stringr/vignettes/stringr.html
https://github.com/tidyverse/dplyr
https://cran.r-project.org/web/packages/broom/vignettes/broom.html
https://cran.r-project.org/web/packages/roxygen2/vignettes/roxygen2.html
http://tibble.tidyverse.org/
https://blog.rstudio.com/2016/03/29/feather/
https://blog.rstudio.com/2016/08/31/forcats-0-1-0/
https://github.com/tidyverse/hms
https://github.com/trestletech/plumber
https://github.com/r-lib/testthat
http://purrr.tidyverse.org/


# broom

summarizes key information about models

https://broom.tidyverse.org/index.html












## abind


## acepack


## addinexamples


## additivityTests


## ade4


## AER


## afex


## AlgDesign


## alluvial


## alr4


## animation


## ANTsR


## ANTsRCore


## anytime


## apaTables


## aplpack


## arm


## arsenal


## ash


## assertthat


## aws.s3


## aws.signature


## backports


## base


## base64enc


## BayesFactor


## bayesplot


## BCA


## BcDiag


## BDgraph


## bdsmatrix


## BH


## BiasedUrn


## BiBitR


## bibtex


## biclust


## bindr


## bindrcpp


## BiocGenerics


## BiocInstaller


## biostatmethods


## bit


## bit64


## bitops


## blob


## blogdown


## bookdown


## boot


## brew


## bridgesampling


## brms


## Brobdingnag


## broom


## BsMD


## ca


## cairoDevice


## callr


## car


## carData


## caTools


## cellranger


## checkmate


## class


## classInt


## cli


## clipr


## clisymbols


## clue


## cluster


## clv


## cmaker


## cmprsk


## coauthornetwork


## cobs


## coda


## CodeDepends


## codetools


## coin


## colorspace


## colourpicker


## combinat


## commonmark


## compiler


## conf.design


## config


## conflicted


## contfrac


## corpcor


## covr


## cowplot


## coxme


## cramer


## crayon


## cronR


## crosstalk


## csvy


## curl


## d3Network


## data.table


## data.tree


## datapasta

https://github.com/MilesMcBain/datapasta

## datasets


## date


## DBI


## dbplyr


## debugme


## Deducer


## DeducerExtras


## demography


## dendextend


## DEoptimR


## depthTools


## desc


## descr


## DescTools


## deSolve


## devtools


## DiagrammeR


## DiceDesign


## dichromat


## digest


## diptest


## DoE.base


## DoE.wrapper


## doParallel


## downloader


## dplyr


## DT


## dtplyr


## dunn.test


## dygraphs


## e1071


## EcoVirtual


## effects


## effsize


## ellipse


## elliptic


## emmeans


## enc


## ENmisc


## Epi


## epibasix


## epiDisplay


## epiR


## epitools


## estimability


## etm


## evaluate


## exact2x2


## exactci


## exactRankTests


## experiment


## expm


## extrantsr


## ez


## FactoMineR


## Fahrmeir


## fansi


## fastmatch


## fBasics


## fda


## fdrtool


## feather


## ff


## ffbase


## finalfit


## fit.models


## fivethirtyeight


## flashClust


## flatxml


## flexclust


## flexmix


## flextable


## FNN


## forcats


## foreach


## forecast


## forecastHybrid


## foreign


## formatR


## formattable


## Formula


## fpc


## fracdiff


## FrF2


## fslr


## fst


## ftsa


## gdata


## gdtools


## gee


## getPass


## GGally


## ggcorrplot


## ggdendro


## ggExtra


## ggforce


## ggformula


## ggfortify


## ggm


## ggplot2


## ggplot2movies


## ggpubr


## ggraph


## ggrepel


## ggridges


## ggsci


## ggsignif


## ggstance


## ggstatsplot


## ggthemes


## ggvis


## gh


## git2r


## glasso


## glmmTMB


## glue


## gmailr


## gmodels


## gmp


## gnm


## googleVis


## GPArotation


## gplots


## graph


## graphics


## graphTweets


## grDevices


## grid


## gridExtra


## gsl


## gss


## gtable


## gtools


## gWidgets


## gWidgetstcltk


## GWRM


## h2o


## hash


## haven


## hdrcde


## hexbin


## HH


## highlight


## highr


## Hmisc


## hms


## htmlTable


## htmltools


## htmlwidgets


## httpuv


## httr


## huge


## hunspell


## hypergeo


## ICC


## IRdisplay


## IRkernel


## ISLR


## ISwR


## ITKR


## igraph


## influenceR


## ini


## inline


## ipred


## irlba


## irr


## iterators


## JavaGD


## JGR


## jmv


## jmvcore


## jmvconnect

https://cran.r-project.org/package=jmvconnect


## jomo


## jose


## jpeg


## jsonlite


## kableExtra


## kernlab


## KernSmooth


## klaR


## km.ci


## KMsurv


## knitr


## kohonen


## ks


## labeling


## labelled


## Lahman


## later


## lattice


## latticeExtra


## lava


## lavaan


## lazyeval


## leaps


## lfstat


## lhs


## lintr


## lisrelToR


## lme4


## lmerTest


## lmom


## lmomRFA


## lmtest


## locfit


## loo


## lpSolve


## lubridate


## MAd


## magic


## magicfor


https://cran.r-project.org/web/packages/magicfor/vignettes/magicfor.html


```{r}
magicfor::magic_for(silent = TRUE)

for (i in 1:3) {
  squared <- i ^ 2
  cubed <- i ^ 3
  put(squared, cubed)
}

magicfor::magic_result_as_dataframe()
```



## magrittr


## manipulate


## manipulateWidget


## mapproj


## maps


## maptools


## markdown


## MASS


## Matrix


## matrixcalc


## MatrixModels


## matrixStats


## maxstat


## MBESS


## mc2d


## mclust


## memisc


## memoise


## meta


## metafor


## methods


## mgcv


## mi


## mice

http://www.stefvanbuuren.nl/mi/FIMD.html

- Flexible Imputation of Missing Data

https://stefvanbuuren.name/fimd/

## microbenchmark


## mime


## miniUI


## minpack.lm


## minqa


## misc3d


## mitml


## mixlm


## mixOmics


## mlbench


## mnormt


## modelr


## modeltools


## mosaic

https://github.com/ProjectMOSAIC/mosaic/blob/master/vignettes/mosaic-resources.Rmd

http://mosaic-web.org/


## mosaicCore


## mosaicData


## multcomp


## multcompView


## multicool


## MuMIn


## munsell


## mvnormtest


## mvtnorm


## network


## networkD3


## neurobase


## neuroim


## nFactors


## nleqslv


## nlme


## nloptr


## NLP


## nnet


## nortest


## nparLD


## numbers


## numDeriv


## nycflights13


## OceanView


## officer


## OpenMx


## openssl


## openxlsx


## OptimClassifier


## ordinal


## orloca


## orloca.es


## oro.dicom


## oro.nifti


## packagefinder


## packrat


## pacman


## pan


## pander


## papeR


## parallel


## party


## pbapply


## pbdZMQ


## pbivnorm


## pbkrtest


## pcaPP


## permute


## phia


## pillar


## pkgbuild


## pkgconfig


## pkgload


## PKI


## plogr


## plot3D


## plot3Drgl


## plotly


## pls


## plyr


## PMCMR


## png


## popEpi


## ppcor


## prabclus


## pracma


## praise


## prediction


## prettydoc


## prettyR


## prettyunits


## pROC


## processx


## prodlim


## progress


## promises


## pspearman


## psych


## psycho


## pubh


## purrr


## purrrlyr


## pwr


## qgraph


## quadprog


## quantmod


## quantreg


## questionr


## qvcalc


## R.cache


## R.matlab


## R.methodsS3


## R.oo


## R.utils


## R2HTML


## R6


## rainbow


## rainfreq


## randomcoloR


## randtests


## ranger


## RApiDatetime


## rappdirs


## rARPACK


## raster


## rattle


## rCharts


## rcmdcheck


## Rcmdr


## RcmdrMisc


## RcmdrPlugin.aRnova


## RcmdrPlugin.BCA


## RcmdrPlugin.BiclustGUI


## RcmdrPlugin.coin


## RcmdrPlugin.depthTools


## RcmdrPlugin.DoE


## RcmdrPlugin.doex


## RcmdrPlugin.EACSPIR


## RcmdrPlugin.EBM


## RcmdrPlugin.EcoVirtual


## RcmdrPlugin.epack


## RcmdrPlugin.Export


## RcmdrPlugin.EZR


## RcmdrPlugin.FactoMineR


## RcmdrPlugin.FuzzyClust


## RcmdrPlugin.GWRM


## RcmdrPlugin.HH


## RcmdrPlugin.IPSUR


## RcmdrPlugin.KMggplot2


## RcmdrPlugin.lfstat


## RcmdrPlugin.MA


## RcmdrPlugin.mosaic


## RcmdrPlugin.MPAStats


## RcmdrPlugin.NMBU


## RcmdrPlugin.OptimClassifier


## RcmdrPlugin.orloca


## RcmdrPlugin.PcaRobust


## RcmdrPlugin.plotByGroup


## RcmdrPlugin.pointG


## RcmdrPlugin.qual


## RcmdrPlugin.RiskDemo


## RcmdrPlugin.RMTCJags


## RcmdrPlugin.ROC


## RcmdrPlugin.sampling


## RcmdrPlugin.SCDA


## RcmdrPlugin.SLC


## RcmdrPlugin.SM


## RcmdrPlugin.sos


## RcmdrPlugin.steepness


## RcmdrPlugin.survival


## RcmdrPlugin.sutteForecastR


## RcmdrPlugin.TeachingDemos


## RcmdrPlugin.temis


## RcmdrPlugin.UCA


## RColorBrewer


## Rcpp


## RcppArmadillo


## RcppEigen


## RCurl


## readODS


## readr


## readstata13


## readxl


## RefManageR


## relimp


## rematch


## rematch2


## remotes


## repr


## reprex


## reshape


## reshape2


## ResourceSelection


## rex


## rgexf


## rgl


## RGtk2


## rhandsontable


## RISmed


## rio


## rjags


## rJava


## rjson


## RJSONIO


## rlang


## rmarkdown


## rmatio


## rmdformats


## rmeta


## Rmpfr


## RMySQL


## RNifti


## robets


## robust


## robustbase


## rockchalk


## ROCR


## Rook


## roomba


## roxygen2


## rpart


## rpart.plot


## rpf


## RPostgreSQL


## rprojroot


## rrcov


## rsconnect


## rsm


## RSpectra


## RSQLite


## rstan


## rstanarm


## rstantools


## rstudioapi


## RStudioConsoleRender


## rsvd


## Rtsne


## rtweet


## runjags


## RVAideMemoire


## rversions


## rvest


## s4vd


## sampling


## sandwich


## scales


## scatr


## scatterplot3d


## scholar


## SCMA


## SCRT


## SCVA


## sde


## SDMTools


## selectr


## sem


## SemiCompRisks


## semPlot


## semTools


## sendmailR


## servr


## sessioninfo


## sf


## sfsmisc


## shape


## shiny


## shinyFiles


## shinyjs


## shinystan


## shinythemes


## sjlabelled


## sjmisc


## sjstats


## skimr


## slam


## SLC


## Sleuth2


## smcure


## sna


## snakecase


## som


## sos


## sourcetools


## sp


## sparklyr


## SparseM


## spatial


## spData


## splines


## splitstackshape


## SQUAREM


## ssanv


## ssgraph


## stabledist


## StanHeaders


## stapler


## stargazer


## statisticalModeling


## statnet.common


## stats


## stats4


## steepness


## stencila


## stringdist


## stringi


## stringr


## strucchange


## styler


## superbiclust


## SuppDists


## survey


## survival


## survminer


## survMisc


## sutteForecastR


## svglite


## tableone

https://cran.r-project.org/web/packages/tableone/vignettes/introduction.html



## tables


## tabplot


## tangram

https://github.com/spgarbet/tangram

https://cran.r-project.org/web/packages/tangram/index.html

https://cran.r-project.org/web/packages/tangram/vignettes/summary-example.html


- Global Style for Rmd Example


     <style type="text/css">
     \```{r, results='asis'}
     cat(custom_css("lancet.css"))
     ```
     .figbody thead
     {
       background: #aaffff !important;
     }
     .figbody tbody .odd
     {
       background: #aaffff !important;
     }
     </style>
 


https://cran.r-project.org/web/packages/tangram/vignettes/fda-example.html

https://cran.r-project.org/web/packages/tangram/vignettes/example.html


 

https://cran.r-project.org/web/packages/tangram/vignettes/single-style.html


## tcltk


## tcltk2


## TeachingDemos


## testit


## testthat


## TH.data


## threejs


## tibble


## tidygraph


## tidyr


## tidyselect


## tidyverse


## timeDate


## timeSeries


## tinytex


## tkrplot


## tm


## TMB


## tools


## tree


## triebeard


## trimcluster


## tseries


## TTR


## tufterhandout


## tutorial


## tweenr


## ucminf


## units


## updateR


## urca


## urltools


## uroot


## userfriendlyscience


## usethis


## utf8


## utils


## uuid


## V8


## vcd


## vcdExtra


## vegan


## VGAM


## ViewPipeSteps

https://github.com/daranzolin/ViewPipeSteps



## viridis


## viridisLite


## visdat


## visNetwork


## visreg


## wbstats


## webshot


## whisker


## WhiteStripe


## withr


## wordcloud


## workflowr


## writexl


## WRS2


## xfun


## XLConnect


## XLConnectJars


## xlsx


## xlsxjars


## XML


## xml2


## xplain


## xray


## xtable


## xts


## yaImpute


## yaml


## zip


## zoo



## Effsize

a package for efficient effect size computation

https://github.com/mtorchiano/effsize


