---
title: "R Packages Used"
output: html_notebook
---

<!-- ```{r setup, cache = F, warning = FALSE} -->

<!-- knitr::opts_chunk$set( -->
<!-- 	error = TRUE, -->
<!-- 	message = FALSE, -->
<!-- 	warning = FALSE, -->
<!-- 	eval = FALSE, -->
<!-- 	include = TRUE -->
<!-- ) -->
<!-- ``` -->


# infer
Tidy Statistical Inference
https://cran.r-project.org/web/packages/infer/index.html

https://kbroman.org/pkg_primer/

## Packages to be studied


```{r}
packagefinder::findPackage(c("pubmed", "bibliography"))
```

https://cran.rstudio.com/web/packages/sys/

# scales

Scale Functions for Visualization

https://cran.r-project.org/web/packages/scales/index.html

```{r}
paste0(round(.20394*100, 1), "%")
scales::percent(.20394)
```


# animation
A Gallery of Animations in Statistics and Utilities to Create Animations
https://cran.r-project.org/web/packages/animation/

# gganimate
A Grammar of Animated Graphics
https://github.com/thomasp85/gganimate


https://cran.r-project.org/web/packages/naniar/index.html

https://hughjonesd.github.io/anim.plots/anim.plots.html

You Can Design a Good Chart with R
https://towardsdatascience.com/you-can-design-a-good-chart-with-r-5d00ed7dd18e

Bubble-grid-maps
https://jschoeley.github.io/2018/06/30/bubble-grid-map.html

Taking control of animations in R and demystifying them in the process 
https://www.data-imaginist.com/2017/animating-the-logo/?utm_content=bufferd418f&utm_medium=social&utm_source=twitter.com&utm_campaign=buffer
 
https://cran.r-project.org/web/packages/rticles/rticles.pdf



https://colinfay.me/build-api-wrapper-package-r/

https://www.datacamp.com/community/tutorials/setup-data-science-environment

https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html####installation

https://cran.r-project.org/web/packages/expss/vignettes/tables-with-labels.html

https://cran.r-project.org/web/packages/tabulizer/vignettes/tabulizer.html

https://github.com/benjaminrich/table1

https://cran.r-project.org/web/packages/tableone/vignettes/introduction.html

https://twitter.com/mitchoharawild/status/1007297976711110659?s=12

https://twitter.com/mf_viz/status/1004954297962917891?s=12

https://github.com/cmap/morpheus.R

https://github.com/talgalili/heatmaply/

https://github.com/rstudio/d3heatmap

http://worksmarter.pl/en/post/webscraping-case-study-1/

http://worksmarter.pl/en/post/job-automation-r-1/

http://www.brodrigues.co/blog/2018-06-10-scraping_pdfs/

https://www.r-bloggers.com/how-to-plot-with-ggiraph/

https://www.r-bloggers.com/understanding-pca-using-stack-overflow-data/

https://www.r-bloggers.com/beautiful-and-powerful-correlation-tables-in-r/

http://journals.plos.org/plosone/article?id=10.1371%2Fjournal.pone.0188299

https://github.com/trinker/reports

Animated Directional Chord Diagrams
https://guyabel.com/post/animated-directional-chord-diagrams/


modelDown: a website generator for your predictive models
http://smarterpoland.pl/index.php/2018/06/modeldown-a-website-generator-for-your-predictive-models/

# drake
https://ropensci.github.io/drake/


## chromoMap

An R package for Interactive visualization and mapping of human chromosomes

https://cran.r-project.org/web/packages/chromoMap/vignettes/chromoMap.html

## tabplot

Tableplot, a Visualization of Large Datasets

https://cran.r-project.org/web/packages/tabplot/index.html

https://cran.r-project.org/web/packages/tabplot/vignettes/tabplot-vignette.html

https://cran.r-project.org/web/packages/tabplot/vignettes/tabplot-timings.html

## treemap

Treemap Visualization

https://cran.r-project.org/web/packages/treemap/index.html

## VIM

Visualization and Imputation of Missing Values

https://cran.r-project.org/web/packages/VIM/index.html

## survey

https://cran.r-project.org/web/packages/survey/index.html

## tidytext

https://cran.r-project.org/web/packages/tidytext/index.html

https://cran.r-project.org/web/packages/tidytext/vignettes/tf_idf.html

https://cran.r-project.org/web/packages/tidytext/vignettes/tidying_casting.html

https://cran.r-project.org/web/packages/tidytext/vignettes/tidytext.html

https://cran.r-project.org/web/packages/tidytext/vignettes/topic_modeling.html


## rapport  an R templating system

http://rapport-package.info/

## ztable

https://github.com/cardiomoon/ztable

## texreg

https://cran.r-project.org/web/packages/texreg/vignettes/texreg.pdf

## SortableHTMLTables

https://cran.r-project.org/web/packages/SortableHTMLTables/index.html

## hwriter

https://cran.r-project.org/web/packages/hwriter/vignettes/hwriter.pdf

## HTMLUtils

https://cran.r-project.org/web/packages/HTMLUtils/index.html

## htmlTable
https://cran.r-project.org/web/packages/htmlTable/index.html

## formattable

https://cran.r-project.org/web/packages/formattable/index.html

## DT

DT: An R interface to the DataTables library

https://rstudio.github.io/DT/

## stargazer

Well-Formatted Regression and Summary Statistics Tables

https://cran.r-project.org/web/packages/stargazer/index.html




## conflicted

## psycho

```{r, eval=FALSE, include=TRUE}
install.packages("devtools")
library("devtools")
install_github("neuropsychology/psycho.R")
library("psycho")
```


## styler

## tidyverse

## splitstackshape

## epiR

Basic Epi

install.packages("epiR")

## lmtest

Some useful epitools especially 2*2 tables and stratified MH Odds

install.packages("lmtest")

## popEpi

install.packages("popEpi")

## Extra tools to go with 'Epi' and make nice rate tables

## survival

install.packages("survival")

for survial analysis, kaplan-meier plots and cox regression

## survminer

install.packages("survminer")

Really nice KM plots!

## Random-Effects Modeks

install.packages("lme4")

install.packages("sjstats")


## Multiple Imputation

install.packages("mice")


install.packages("arsenal")

## Really nice summmary tables

## Complex survey data analysis

install.packages("survey")

## For handling complex survey data

install.packages("ICC")


## Alternative methods for ICC calculation from survey data

## Meta-analysis

install.packages("meta")


install.packages("metafor")


install.packages("workflowr")


install.packages("DiagrammeR")


install.packages("tangram")


devtools::install_github("lbusett/insert_table")


```{r}
#### Obtain names of all packages on CRAN
names.available.packages <- rownames(available.packages())

#### Extract packages names that contain Rcmdr
Rcmdr.related.packages <- names.available.packages[grep("Rcmdr", names.available.packages)]
Rcmdr.related.packages

#### Install these packages
install.packages(pkgs = Rcmdr.related.packages)
```



```{r}
usePackage <- function(p) {
  if (!is.element(p, installed.packages()[, 1])) {
    install.packages(p, dep = TRUE)
  }
  require(p, character.only = TRUE)
}
```



```{r}
file.edit("~/Desktop/foo/.Rprofile")
## This opens up a script window, within which you can enter in your library commands
library(ggplot2)
library(scales)
library(plyr)
library(reshape2)
```






## abind



## acepack



## AlgDesign



## AnnotationDbi



## aplpack



## arm



## assertthat



## backports



## base



## base64enc



## BCA



## BH



## BiasedUrn



## bindr



## bindrcpp



## Biobase



## BiocGenerics



## BiocInstaller



## bit



## bit64



## bitops



## blob



## boot



## broom



## BsMD



## ca



## car



## caTools



## cellranger



## checkmate



## class



## cluster



## clv



## coda



## codetools



## coin



## colorspace



## combinat



## compiler



## conf.design



## curl



## data.table



## datasets



## date



## DBI



## deldir



## depthTools



## DiceDesign



## dichromat



## digest



## DoE.base



## DoE.wrapper



## doParallel



## dplyr



## e1071



## effects



## ENmisc



## epiR



## estimability



## evaluate



## ez



## flexclust



## forcats



## foreach



## foreign



## formatR



## Formula



## fracdiff



## FrF2



## gdata



## ggplot2

http://www.cookbook-r.com/Graphs/

### ggplot2 extensions

http://www.ggplot2-exts.org/gallery/

http://corybrunson.github.io/ggalluvial/

http://www.sthda.com/english/rpkgs/survminer/

## ggthemes



## ggvis



## glue



## goftest



## graphics



## grDevices



## grid



## gridBase



## gridExtra



## gtable



## gtools



## haven



## highr



## Hmisc



## hms



## htmlTable



## htmltools



## htmlwidgets



## httpuv



## httr



## igraph



## IRanges



## irlba



## iterators



## jsonlite



## KernSmooth



## knitr



## labeling



## lattice



## latticeExtra



## lazyeval



## leaps



## lhs



## lme4



## lmtest



## lsmeans



## lubridate



## magrittr



## markdown



## MASS



## Matrix



## matrixcalc



## MatrixModels



## memoise



## methods



## mgcv



## mi



## mime



## minqa



## mnormt



## modelr



## modeltools



## multcomp



## munsell



## mvtnorm



## nlme



## nloptr



## NLP



## NMF



## nnet



## nortest



## openssl



## ordinal



## orloca



## orloca.es



## parallel



## pbkrtest



## pkgconfig



## pkgmaker



## plogr



## plyr



## polyclip



## psych



## purrr



## quadprog



## quantmod



## quantreg



## R2HTML



## R6



## randtests



## Rcmdr



## RcmdrMisc



## RcmdrPlugin.BCA



## RcmdrPlugin.coin



## RcmdrPlugin.depthTools



## RcmdrPlugin.DoE



## RcmdrPlugin.doex



## RcmdrPlugin.EACSPIR



## RcmdrPlugin.EBM



## RcmdrPlugin.epack



## RcmdrPlugin.EZR



## RcmdrPlugin.KMggplot2



## RcmdrPlugin.mosaic



## RcmdrPlugin.MPAStats



## RcmdrPlugin.orloca



## RcmdrPlugin.plotByGroup



## RcmdrPlugin.qual



## RcmdrPlugin.SCDA

## RcmdrPlugin.sampling

Tools for sampling in Official Statistical Surveys

https://cran.r-project.org/web/packages/RcmdrPlugin.sampling/index.html


## RcmdrPlugin.seeg



## RcmdrPlugin.SLC



## RcmdrPlugin.SM



## RcmdrPlugin.steepness



## RcmdrPlugin.survival



## RcmdrPlugin.TeachingDemos



## RcmdrPlugin.temis



## RcmdrPlugin.UCA



## RColorBrewer



## Rcpp



## RcppArmadillo



## RcppEigen



## readr



## readxl



## registry



## relimp



## rematch



## reshape



## reshape2



## rgl



## RISmed



## rJava



## rlang



## rmarkdown



## RMySQL



## rngtools



## rpart



## rpart.plot



## rprojroot



## rsm



## RSQLite



## rvest



## S4Vectors



## sandwich



## scales



## scatterplot3d



## SCMA



## SCRT



## SCVA



## seeg



## selectr



## sem



## sfsmisc



## sgeostat



## shiny



## shinythemes



## slam



## SLC



## sourcetools



## SparseM



## spatial



## spatstat



## spatstat.utils



## splines



## stats



## stats4



## steepness



## stringi



## stringr



## survival



## tcltk



## tcltk2



## TeachingDemos



## tensor



## TH.data



## tibble



## tidyr



## tidyverse



## timeDate



## tkrplot



## tm



## tools



## tseries



## TTR



## ucminf



## utils



## vcd



## viridis



## viridisLite



## XLConnect



## XLConnectJars



## xml2



## xtable



## xts



## yaml



## zoo















install.packages("stargazer")

install.packages("pander")

install.packages("tables")

install.packages("ascii")

install.packages("xtable")

devtools::install_github("hadley/dplyr")


install.packages("gapminder")

install.packages("alluvial")


vignette("databases", package = "dplyr")

install.packages("robustbase")

install.packages("insuranceData")

install.packages("Lahman")


install.packages("tidyverse")

install.packages("qdap")

install.packages("openxlsx")


devtools::install_github("kassambara/r2excel")

install.packages("WriteXLS")

install.packages("XLConnect")

library(XLConnect)


```{r}
if (!require(wordcloud)) {
  install.packages("wordcloud")
  library(wordcloud)
}
```



```{r}
installed <- as.data.frame(installed.packages())
write.csv(installed, "installed_previously.csv")

installedPreviously <- read.csv("installed_previously.csv")
baseR <- as.data.frame(installed.packages())
toInstall <- setdiff(installedPreviously, baseR)

install.packages(toInstall)


packagelist <- installed.packages()
class(packagelist)
packagelist[, 1]
```




## Rcmdr

```{r}
install.packages("Rcmdr")
install.packages("RcmdrPlugin.BCA")
install.packages("RcmdrPlugin.coin")
install.packages("RcmdrPlugin.depthTools")
install.packages("RcmdrPlugin.doBy")
install.packages("RcmdrPlugin.DoE")
install.packages("RcmdrPlugin.doex")
install.packages("RcmdrPlugin.EACSPIR")
install.packages("RcmdrPlugin.EBM")
install.packages("RcmdrPlugin.epack")
install.packages("RcmdrPlugin.EZR")
install.packages("RcmdrPlugin.HH")
install.packages("RcmdrPlugin.IPSUR")
install.packages("RcmdrPlugin.KMggplot2")
install.packages("RcmdrPlugin.mosaic")
install.packages("RcmdrPlugin.MPAStats")
install.packages("RcmdrPlugin.orloca")
install.packages("RcmdrPlugin.plotByGroup")
install.packages("RcmdrPlugin.qcc")
install.packages("RcmdrPlugin.qual")
install.packages("RcmdrPlugin.SCDA")
install.packages("RcmdrPlugin.seeg")
install.packages("RcmdrPlugin.SLC")
install.packages("RcmdrPlugin.SM")
install.packages("RcmdrPlugin.StatisticalURV")
install.packages("RcmdrPlugin.steepness")
install.packages("RcmdrPlugin.survival")
install.packages("RcmdrPlugin.TeachingDemos")
install.packages("RcmdrPlugin.temis")
install.packages("RcmdrPlugin.UCA")
```


```{r}
source("https://bioconductor.org/biocLite.R")
biocLite()
```


install.packages("tidyverse")

install.packages("devtools")

devtools::install_github("hadley/colformat")

devtools::install_github("ropenscilabs/skimr")

install.packages("hflights")

install.packages("dbplyr")

install.packages("xlsx")

require(devtools)

install_github("ProjectMOSAIC/mosaic")

install.packages("jmv")


install.packages("wordcloud")

install.packages("https://cran.r-project.org/src/contrib/Archive/tm/tm_0.6.tar.gz", repos = NULL)

install.packages("SnowballC")

install.packages("RColorBrewer")

install.packages("tidytext")

install.packages("packrat")

install.packages("testthat")

install.packages("prettydoc")

install.packages("rmdformats")

install.packages(c("fivethirtyeight", "tidyverse", "knitr", "kableExtra", "ggthemes"))

library(devtools)

install_github("SPSStoR", username = "lebebr01")

library(SPSStoR)


```{r}
ip <- installed.packages()
pkgs.to.remove <- ip[!(ip[, "Priority"] %in% c("base", "recommended")), 1]
sapply(pkgs.to.remove, remove.packages)
sapply(pkgs.to.remove, install.packages)
```




```{r}
install.packages("devtools")
devtools::install_github("AndreaCirilloAC/updateR")
library(updateR)
updateR(admin_password = "") ## Where "PASSWORD" stands for your system password

```






survival

survminer

install.packages("tutorial")


devtools::install_github("romainfrancois/highlight")

install.packages("highr", repos = "http://rforge.net", type = "source")



install.packages("xplain")





```{r remove all user installed packages in R, eval=FALSE, include=TRUE}
## How to remove all user installed packages in R
## https://www.r-bloggers.com/how-to-remove-all-user-installed-packages-in-r/

## create a list of all installed packages
ip <- as.data.frame(installed.packages())
head(ip)
## if you use MRO, make sure that no packages in this library will be removed
ip <- subset(ip, !grepl("MRO", ip$LibPath))
## we don't want to remove base or recommended packages either\
ip <- ip[!(ip[,"Priority"] %in% c("base", "recommended")),]
## determine the library where the packages are installed
path.lib <- unique(ip$LibPath)
## create a vector with all the names of the packages you want to remove
pkgs.to.remove <- ip[,1]
head(pkgs.to.remove)
## remove the packages
sapply(pkgs.to.remove, remove.packages, lib = path.lib)
```


## Schedule R Script

library(knitr)

library(markdown)
 

knit("SchedulePubMedAnalysis.Rmd")

markdownToHTML("SchedulePubMedAnalysis.md", "docs/SchedulePubMedAnalysis.html")

setwd("~")

file.choose()

library(rmarkdown)


Preperation Packages Schedule R Script

 https://github.com/jkeirstead/scholar

 http://rogiersbart.blogspot.com.tr/2015/05/put-google-scholar-citations-on-your.html

 http://tuxette.nathalievilla.org/?p=1682

 https://github.com/sunitj/scholar

 https://tgmstat.wordpress.com/2013/09/11/schedule-rscript-with-cron/

 https://github.com/ropensci/git2r
     

 library(knitr)

 library(markdown)
 
 install.packages('data.table')

 install.packages('knitr')

 install.packages('miniUI')

 install.packages('shiny')

 install.packages('shinyFiles')
 
 install.packages("taskscheduleR", repos = "http://www.datatailor.be/rcube", type = "source")
 
 devtools::install_github("bnosac/cronR")

 install.packages('scholar')
 
 
 install.packages("git2r")


## flatxml

http://www.zuckarelli.de/flatxml/articles/example/example.html

```{r}
xmldata <- flatxml::fxml_importXMLFlat("data/PathologyTurkey.xml")

```


## roomba

General purpose API response tidier

https://github.com/ropenscilabs/roomba/

```{r}
roomba::shiny_roomba()
```



## tufterhandout

Tufte-style html document format for rmarkdown

https://cran.r-project.org/web/packages/tufterhandout/index.html

```{r}
## install.packages("tufterhandout")
library(tufterhandout)
```

## papeR

[https://sbalci.github.io/MyRCodesForDataAnalysis/papeR.nb.html](https://sbalci.github.io/MyRCodesForDataAnalysis/papeR.nb.html)

## tm

install.packages("tm")

https://cran.r-project.org/web/packages/tm/vignettes/tm.pdf

---

https://atom.io/packages/hydrogen


---

R Package Documentation
https://rdrr.io/
R Packages Search and Statistics
https://www.rpackages.io/
ReporteRs is an R package for creating Microsoft Word and Powerpoint documents.
https://davidgohel.github.io/ReporteRs/
officer Manipulation of Microsoft Word and PowerPoint Documents
https://cran.r-project.org/web/packages/officer/
pubh
https://cran.rstudio.com/web/packages/pubh/vignettes/introduction.html
What does visdat do?
Initially inspired by csv-fingerprint, vis_dat helps you visualise a dataframe and “get a look at the data” by displaying the variable classes in a dataframe as a plot with vis_dat, and getting a brief look into missing data patterns using vis_miss.
https://www.tidyverse.org/
https://cran.r-project.org/web/packages/shiny/index.html
https://rmarkdown.rstudio.com/
http://ggplot2.org/
https://yihui.name/knitr/
http://vita.had.co.nz/papers/tidy-data.html
https://blog.rstudio.com/2015/04/09/readr-0-1-0/
http://readxl.tidyverse.org/
https://cran.r-project.org/web/packages/lubridate/vignettes/lubridate.html
https://github.com/r-lib/devtools
https://cran.r-project.org/web/packages/magrittr/index.html
http://rstudio.github.io/packrat/
https://cran.r-project.org/web/packages/stringr/vignettes/stringr.html
https://github.com/tidyverse/dplyr
https://cran.r-project.org/web/packages/broom/vignettes/broom.html
https://cran.r-project.org/web/packages/roxygen2/vignettes/roxygen2.html
http://tibble.tidyverse.org/
https://blog.rstudio.com/2016/03/29/feather/
https://blog.rstudio.com/2016/08/31/forcats-0-1-0/
https://github.com/tidyverse/hms
https://github.com/trestletech/plumber
https://github.com/r-lib/testthat
http://purrr.tidyverse.org/



