---
title: "My R Codes For Data Analysis"
subtitle: "In this repository I am going to collect `R codes` for data analysis. Codes are from various resources and I try to give original link as much as possible."
author: "[Serdar Balcı, MD, Pathologist](https://www.serdarbalci.com/)"
date: '`r format(Sys.Date())`'
output: 
  html_notebook: 
    fig_caption: yes
    highlight: tango
    number_sections: yes
    theme: paper
    toc: yes
    toc_depth: 5
    toc_float: yes
  html_document: 
    code_folding: hide
    df_print: kable
    keep_md: yes
    number_sections: yes
    theme: cerulean
    toc: yes
    toc_float: yes
    highlight: kate
---

- finalfit


http://www.datasurg.net/2018/07/12/finalfit-now-includes-bootstrap-simulation-for-model-prediction/

- 

https://kbroman.org/knitr_knutshell/pages/figs_tables.html

## Tables

```{r}
library(xtable)
xtable(BMT)
```


```{r}
library(kableExtra)
kable(BMT)
```


```{r display results as table}

require(rhandsontable)
rhandsontable(BMT)

```

## tttable

https://github.com/leeper/tttable







### - renderers

####  - xtable

https://rdrr.io/cran/xtable/man/xtable.html










####  - flextable

https://davidgohel.github.io/flextable/index.html

```{r}

```


https://cran.r-project.org/web/packages/flextable/vignettes/overview.html

```{r}
library(flextable)
library(officer)
```

```{r}
data <- iris[c(1:3, 51:53, 101:104),]

data

```


```{r}
flextable::regulartable(data)

```

```{r}
myft <- regulartable(
  head(mtcars), 
  col_keys = c("am", "carb", "gear", "mpg", "drat" ))
myft
```

```{r}
myft <- theme_vanilla(myft)
myft
```

```{r}
myft <- merge_v(myft, j = c("am", "carb") )
myft
```

```{r}
myft <- set_header_labels( myft, carb = "# carb." )
myft <- width(myft, width = .75) # set width of all columns to .75 in
myft
```

```{r}
myft <- autofit(myft)
myft
```

```{r}
myft <- italic(myft, j = 1)
myft <- bg(myft, bg = "#C90000", part = "header")
myft <- color(myft, color = "white", part = "header")
myft
```


```{r}
myft <- color(myft, ~ drat > 3.5, ~ drat, color = "red")
myft <- bold(myft, ~ drat > 3.5, ~ drat, bold = TRUE)
myft <- autofit(myft)

myft
```

```{r}
library(officer)


ft <- regulartable(head(mtcars))
ft <- theme_booktabs(ft)
ft <- autofit(ft)

ppt <- read_pptx()
ppt <- add_slide(ppt, layout = "Title and Content", master = "Office Theme")
ppt <- ph_with_flextable(ppt, value = ft, type = "body") 

print(ppt, target = "output/example.pptx")

# https://view.officeapps.live.com/op/view.aspx?src=https://davidgohel.github.io/flextable/articles/assets/pptx/example.pptx

```





```{r}
doc <- read_docx()
doc <- body_add_flextable(doc, value = ft)
print(doc, target = "output/example.docx")
```






- Make Beautiful Tables with the Formattable Package

https://www.displayr.com/formattable/?utm_medium=Feed&utm_source=Syndication



















####  - knitr::kable()


####  - formatttable

```{r}
library(formattable)

p <- percent(c(0.1, 0.02, 0.03, 0.12))
p
p + 0.05
max(p)

```

```{r}
balance <- accounting(c(1000, 500, 200, -150, 0, 1200))
balance

balance + 1000

```


```{r}
p <- data.frame(
  id = c(1, 2, 3, 4, 5), 
  name = c("A1", "A2", "B1", "B2", "C1"),
  balance = accounting(c(52500, 36150, 25000, 18300, 7600), format = "d"),
  growth = percent(c(0.3, 0.3, 0.1, 0.15, 0.15), format = "d"),
  ready = formattable(c(TRUE, TRUE, FALSE, FALSE, TRUE), "yes", "no"))
p
print.AsIs(p)
```

```{r}
df <- data.frame(
  id = 1:10,
  name = c("Bob", "Ashley", "James", "David", "Jenny", 
    "Hans", "Leo", "John", "Emily", "Lee"), 
  age = c(28, 27, 30, 28, 29, 29, 27, 27, 31, 30),
  grade = c("C", "A", "A", "C", "B", "B", "B", "A", "C", "C"),
  test1_score = c(8.9, 9.5, 9.6, 8.9, 9.1, 9.3, 9.3, 9.9, 8.5, 8.6),
  test2_score = c(9.1, 9.1, 9.2, 9.1, 8.9, 8.5, 9.2, 9.3, 9.1, 8.8),
  final_score = c(9, 9.3, 9.4, 9, 9, 8.9, 9.25, 9.6, 8.8, 8.7),
  registered = c(TRUE, FALSE, TRUE, FALSE, TRUE, TRUE, TRUE, FALSE, FALSE, FALSE),
  stringsAsFactors = FALSE)
```









```{r}


library(formattable)

formattable(df, list(
  age = color_tile("white", "orange"),
  grade = formatter("span", style = x ~ ifelse(x == "A", 
    style(color = "green", font.weight = "bold"), NA)),
  area(col = c(test1_score, test2_score)) ~ normalize_bar("pink", 0.2),
  final_score = formatter("span",
    style = x ~ style(color = ifelse(rank(-x) <= 3, "green", "gray")),
    x ~ sprintf("%.2f (rank: %02d)", x, rank(-x))),
  registered = formatter("span",
    style = x ~ style(color = ifelse(x, "green", "red")),
    x ~ icontext(ifelse(x, "ok", "remove"), ifelse(x, "Yes", "No")))
))
```



####  - knitLatex



####  - htmlTable


####  - psytabs


####  - SortableHTMLTables


####  - tablaxlsx


####  - table1xls


####  - tableHTML


####  - TableMonster


####  - texreg


####  - ztable


####  - apaStyle


####  - apaTables


####  - apsrtable


####  - DT

https://www.infoworld.com/video/91607/r-tip-quick-interactive-tables


https://rstudio.github.io/DT/


https://datatables.net/


```{r}
# install.packages('DT')
```







### - higher-level functionality

#### - finalfit




https://github.com/ewenharrison/finalfit

http://www.datasurg.net/2018/05/16/elegant-regression-results-tables-and-plots-the-finalfit-package/


```{r}
# devtools::install_github("ewenharrison/finalfit")
# install.packages("rstan")
# install.packages("boot")

library(tidyverse)
library(finalfit)
library(rstan)
library(boot)

```




```{r}
# Load example dataset, modified version of survival::colon
data(colon_s)



colon_s2$age <- as.numeric(colon_s$age)
colon_s2$age.factor <- as_factor(colon_s$age.factor)
colon_s2$sex.factor <- as_factor(colon_s$sex.factor)
colon_s2$obstruct.factor <- as_factor(colon_s$obstruct.factor)
colon_s2$perfor.factor <- as_factor(colon_s$perfor.factor)
colon_s2$mort_5yr <- as_factor(colon_s$mort_5yr)
colon_s2$hospital <- as_factor(colon_s$hospital)
colon_s2$status <- as.numeric(colon_s$status)
colon_s2$time <- as.numeric(colon_s$time)
colon_s2


```


```{r}
# Table 1 - Patient demographics by variable of interest ----
explanatory = c("age", "age.factor", 
  "sex.factor", "obstruct.factor")
dependent = "perfor.factor" # Bowel perforation
table <- colon_s2 %>%
  summary_factorlist(dependent, explanatory,
  p=TRUE, add_dependent_label=TRUE, total_col = TRUE)

print.AsIs(table)



```




```{r}
# Table 2 - 5 yr mortality ----
explanatory = c("age.factor", 
  "sex.factor",
  "obstruct.factor")
dependent = 'mort_5yr'
table <- colon_s %>%
  summary_factorlist(dependent, explanatory, 
  p=TRUE, add_dependent_label=TRUE)

print.AsIs(table)

```




```{r results='asis'}
knitr::kable(table, row.names=FALSE, 
    align=c("l", "l", "r", "r", "r", "r"))
```



```{r}
explanatory = c("age.factor", "sex.factor", 
  "obstruct.factor", "perfor.factor")
dependent = 'mort_5yr'
table_surv <- colon_s2 %>%
  finalfit(dependent, explanatory)
```




```{r results='asis'}
knitr::kable(table_surv, row.names = FALSE, 
    align = c("l", "l", "r", "r", "r", "r"))
```


```{r}
explanatory = c("age.factor", "sex.factor", 
  "obstruct.factor", "perfor.factor")
explanatory_multi = c("age.factor", 
  "obstruct.factor")
dependent = 'mort_5yr'
colon_s2 %>%
  finalfit(dependent, explanatory, 
  explanatory_multi)
```




```{r}
explanatory = c("age.factor", "sex.factor", 
  "obstruct.factor", "perfor.factor")
explanatory_multi = c("age.factor", "obstruct.factor")
random_effect = "hospital"
dependent = 'mort_5yr'
colon_s2 %>%
  finalfit(dependent, explanatory, 
  explanatory_multi, random_effect)
```




```{r}

explanatory = c("age.factor", "sex.factor", 
"obstruct.factor", "perfor.factor")
dependent = "Surv(time, status)"
colon_s2 %>%
  finalfit(dependent, explanatory)
```





```{r}
explanatory = c("age.factor", "sex.factor", 
  "obstruct.factor", "perfor.factor")
dependent = 'mort_5yr'
table7 <- colon_s2 %>%
  finalfit(dependent, explanatory, 
  metrics=TRUE)
```





```{r, echo=FALSE, results="asis"}
knitr::kable(table7[[1]], row.names=FALSE, align=c("l", "l", "r", "r", "r"))
knitr::kable(table7[[2]], row.names=FALSE)
```





```{r}
explanatory = c("age.factor", "sex.factor", 
  "obstruct.factor", "perfor.factor")
explanatory_multi = c("age.factor", "obstruct.factor")
random_effect = "hospital"
dependent = 'mort_5yr'

# Separate tables
colon_s2 %>%
  summary_factorlist(dependent, 
  explanatory, fit_id=TRUE) -> example.summary

colon_s2 %>%
  glmuni(dependent, explanatory) %>%
  fit2df(estimate_suffix=" (univariable)") -> example.univariable

colon_s2 %>%
  glmmulti(dependent, explanatory) %>%
  fit2df(estimate_suffix=" (multivariable)") -> example.multivariable

colon_s2 %>%
  glmmixed(dependent, explanatory, random_effect) %>%
  fit2df(estimate_suffix=" (multilevel)") -> example.multilevel

# Pipe together
example.summary %>%
  finalfit_merge(example.univariable) %>%
  finalfit_merge(example.multivariable) %>%
  finalfit_merge(example.multilevel) %>%
  select(-c(fit_id, index)) %>% # remove unnecessary columns
  dependent_label(colon_s2, dependent, prefix="") # place dependent variable label
```







```{r fig.height=5, fig.width=6}
# OR plot
explanatory = c("age.factor", "sex.factor", 
  "obstruct.factor", "perfor.factor")
dependent = 'mort_5yr'
colon_s2 %>%
  or_plot(dependent, explanatory)
# Previously fitted models (`glmmulti()` or 
# `glmmixed()`) can be provided directly to `glmfit`
```


```{r fig.height=5, fig.width=6}
# HR plot
explanatory = c("age.factor", "sex.factor", 
  "obstruct.factor", "perfor.factor")
dependent = "Surv(time, status)"
colon_s2 %>%
  hr_plot(dependent, explanatory, dependent_label = "Survival")
# Previously fitted models (`coxphmulti`) can be provided directly using `coxfit`
```


```{r}
# KM plot
explanatory = c("perfor.factor")
dependent = "Surv(time, status)"

plotKM <- colon_s2 %>%
  surv_plot(dependent, explanatory, 
  xlab = "Time (days)", pval = TRUE, legend = "none")

plotKM

```




















####   - janitor


####   - huxtable

https://hughjonesd.github.io/huxtable/design-principles.html



####   - tables


####   - stargazer


####   - pixiedust

pixiedust: Tables so Beautifully Fine-Tuned You Will Believe It's Magic

https://cran.r-project.org/web/packages/pixiedust/vignettes/pixiedust.html

https://cran.r-project.org/web/packages/pixiedust/vignettes/advancedMagic.html






####   - reporttools


####   - rtable


####   - summarytools


####   - tab


####   - tableone


####   - carpenter


https://cran.r-project.org/web/packages/carpenter/vignettes/carpenter.html



####   - dtables


####   - etable

####   - tangram
tangram (grammar of tables)

https://github.com/spgarbet/tangram
http://htmlpreview.github.io/?https://github.com/spgarbet/tg/blob/master/vignettes/example.html

https://github.com/spgarbet/tangram/issues/36


<!-- library(tangram) -->
<!-- library(Hmisc) -->
<!-- getHdata(pbc) -->
<!-- View(pbc) -->
<!-- table <- tangram(drug ~ bili + albumin + stage + protime + sex + age + spiders, data = pbc) -->

<!-- table -->
<!-- html5(table) -->
<!-- latex(table) -->
<!-- index(table) -->

<!-- write( -->
<!-- html5(tangram("drug ~ bili[2] + albumin + stage::Categorical + protime + sex + age + spiders", pbc, msd=TRUE, quant=seq(0, 1, 0.25)), -->
<!--       fragment=TRUE, inline="hmisc.css", caption = "HTML5 Table Hmisc Style", id="tbl2"), -->
<!-- "tangram1.html") -->

<!-- write( -->
<!-- html5(tangram("drug ~ bili[2] + albumin + stage::Categorical + protime + sex + age + spiders", pbc), -->
<!--       fragment=TRUE, inline="nejm.css", caption = "HTML5 Table NEJM Style", id="tbl3"), -->
<!-- "tangram_nejm.html") -->


<!-- tbl <- tangram("drug ~ bili[2] + albumin + stage::Categorical[1] + protime + sex[1] + age + spiders[1]",  -->
<!--                data=pbc, -->
<!--                pformat = 5) -->
<!-- write(html5(tbl, -->
<!--       fragment=TRUE, -->
<!--       inline="lancet.css", -->
<!--       caption = "HTML5 Table Lancet Style", id="tbl4" -->
<!-- ), -->
<!-- "tangram_lancet.html") -->

<!-- index(tangram("drug ~ bili + albumin + stage::Categorical + protime + sex + age + spiders", pbc))[1:20,] -->


<!-- library(readxl) -->
<!-- MDL307_Data <- read_excel("MDL307 - Data.xlsx") -->

<!-- MDL307_Data <- as.data.frame(MDL307_Data) -->

<!-- names(MDL307_Data) -->

<!-- View(MDL307_Data) -->

<!-- MDL307_Data$biyokimyasalrekurrens <- as.factor(MDL307_Data$biyokimyasalrekurrens) -->
<!-- levels(MDL307_Data$biyokimyasalrekurrens)[1] <- "yok" -->
<!-- levels(MDL307_Data$biyokimyasalrekurrens)[2] <- "var" -->

<!-- collist <- c("gleasonskor", -->
<!--                  "tersiyer", -->
<!--                  "kribriform", -->
<!--                  "cerrahisinir", -->
<!--                  "ekstaprostatik", -->
<!--                  "lenfnodu", -->
<!--                  "seminalvezikul" -->
<!--                  ) -->


<!-- MDL307_Data[collist] <- lapply(MDL307_Data[collist], as.factor) -->


<!-- table <- tangram(biyokimyasalrekurrens ~ yas + -->
<!--                  gleasonskor + -->
<!--                  tersiyer + -->
<!--                  kribriform + -->
<!--                  kribriformyuzde + -->
<!--                  cerrahisinir + -->
<!--                  ekstaprostatik + -->
<!--                  lenfnodu + -->
<!--                  seminalvezikul + -->
<!--                  biyokimyasalrekurrens, -->
<!--                  data = MDL307_Data) -->
<!-- table -->


<!-- ## SemiCompRisks -->

<!-- install.packages("SemiCompRisks") -->
<!-- library(SemiCompRisks) -->
<!-- data(BMT) -->

<!-- ## smcure -->

<!-- install.packages("smcure") -->
<!-- library(smcure) -->
<!-- data(e1684) -->




### - pivots


####   - rpivotttable

### - other


####   - gtable


#### - sjtlm
https://strengejacke.github.io/sjPlot/articles/sjtlm.html


#### - arsenal

to compare data frames: https://cran.r-project.org/web/packages/arsenal/vignettes/compare.html

##### - arsenal::paired

summary statistics for a set of variables paired across two time points: 

https://cran.r-project.org/web/packages/arsenal/vignettes/paired.html


```{r}
library(arsenal)
dat <- data.frame(
  tp = paste0("Time Point ", c(1, 2, 1, 2, 1, 2, 1, 2, 1, 2)),
  id = c(1, 1, 2, 2, 3, 3, 4, 4, 5, 6),
  Cat = c("A", "A", "A", "B", "B", "B", "B", "A", NA, "B"),
  Fac = factor(c("A", "B", "C", "A", "B", "C", "A", "B", "C", "A")),
  Num = c(1, 2, 3, 4, 4, 3, 3, 4, 0, NA),
  Ord = ordered(c("I", "II", "II", "III", "III", "III", "I", "III", "II", "I")),
  Lgl = c(TRUE, TRUE, FALSE, TRUE, FALSE, TRUE, TRUE, FALSE, FALSE, FALSE),
  Dat = as.Date("2018-05-01") + c(1, 1, 2, 2, 3, 4, 5, 6, 3, 4),
  stringsAsFactors = FALSE
)
```

```{r}
dat
```


```{r, include=TRUE, comment=NA, prompt=FALSE, cache=FALSE, echo=TRUE, results='asis'}
p <- paired(tp ~ Cat + Fac + Num + Ord + Lgl + Dat, data = dat, id = id, signed.rank.exact = FALSE)
summary(p)
```


##### - arsenal::freqlist

https://cran.r-project.org/web/packages/arsenal/vignettes/freqlist.html

```{r}
require(arsenal)
```


```{r}
# load the data
data(mockstudy)

# retain NAs when creating the table using the useNA argument
tab.ex <- table(mockstudy[, c("arm", "sex", "mdquality.s")], useNA = "ifany")
```


```{r}
tab.ex
```

```{r}
noby <- freqlist(tab.ex)

str(noby)
```

```{r}
# view the data frame portion of freqlist output
head(noby[["freqlist"]])  ## or use as.data.frame(noby)
```


```{r}
summary(noby)
```


summary(noby, title = "Basic freqlist output")

summary(freqlist(~ arm + sex + mdquality.s, data = mockstudy, addNA = TRUE))

summary(freqlist(~arm + sex + addNA(mdquality.s), data = mockstudy))

summary(freqlist(~arm + sex + includeNA(mdquality.s, "Missing"), data = mockstudy))

```
withnames <- freqlist(tab.ex, labelTranslations = c("Treatment Arm", "Gender", "LASA QOL"), digits = 0)
summary(withnames)
```



##### - arsenal::tableby

https://cran.r-project.org/web/packages/arsenal/vignettes/tableby.html


##### - arsenal::modelsum

https://cran.r-project.org/web/packages/arsenal/vignettes/modelsum.html


#### - desctable


https://cran.r-project.org/web/packages/desctable/vignettes/desctable.html


# GT

https://github.com/rstudio/gt


```{r}
install.packages("devtools")
remotes::install_github("rstudio/gt")
```


```{r}
library(gt)
library(tidyverse)
library(glue)

# Define the start and end dates for the data range
start_date <- "2010-06-07"
end_date <- "2010-06-14"

# Create a gt table based on preprocessed
# `sp500` table data
sp500 %>%
  dplyr::filter(date >= start_date & date <= end_date) %>%
  dplyr::select(-adj_close) %>%
  dplyr::mutate(date = as.character(date)) %>%
  gt() %>%
  tab_header(
    title = "S&P 500",
    subtitle = glue::glue("{start_date} to {end_date}")
  ) %>%
  fmt_date(
    columns = vars(date),
    date_style = 3
  ) %>%
  fmt_currency(
    columns = vars(open, high, low, close),
    currency = "USD"
  ) %>%
  fmt_number(
    columns = vars(volume),
    scale_by = 1 / 1E9,
    pattern = "{x}B"
  )
```

