---
title: "Text Mining"
output: html_notebook
---


https://regexr.com/

https://regex101.com/

# Read text files with readtext()

https://cran.r-project.org/web/packages/readtext/vignettes/readtext_vignette.html


# qdapRegex

```{r eval=FALSE, include=FALSE, echo=TRUE}
library(qdapRegex)
```


https://github.com/trinker/qdapRegex

http://trinker.github.io/qdapRegex_dev/index.html

# stringr

https://cran.r-project.org/web/packages/stringr/vignettes/stringr.html

```
stringr::str_view()
```


# RegExplain

https://www.garrickadenbuie.com/project/regexplain/


```{r eval=FALSE, include=FALSE, echo=TRUE}
# devtools::install_github("gadenbuie/regexplain")
# source("https://install-github.me/gadenbuie/regexplain")
```



# A Tidy Text Analysis of My Google Search History

https://www.r-bloggers.com/a-tidy-text-analysis-of-my-google-search-history/



# Text Mining with R A Tidy Approach

https://www.tidytextmining.com/

# Pride and Prejudice

https://juliasilge.com/blog/tidy-text-classification/

https://juliasilge.com/blog/if-i-loved-nlp-less/


# cleanNLP

https://statsmaths.github.io/cleanNLP/

# Text analysis of holy books

## quRan 

https://github.com/andrewheiss/quRan

https://github.com/andrewheiss/quRan/blob/master/data-raw/clean_data.R


### Tidy text, parts of speech, and unique words in the Qur'an

https://www.andrewheiss.com/blog/2018/12/28/tidytext-pos-arabic/


## sacred

http://sacred.john-coene.com/

https://github.com/JohnCoene/sacred

## scriptuRs 

https://github.com/andrewheiss/scriptuRs


### Tidy text, parts of speech, and unique words in the Bible

https://www.andrewheiss.com/blog/2018/12/26/tidytext-pos-john/



```{r eval=FALSE, include=FALSE, echo=TRUE}
# devtools::install_github("andrewheiss/scriptuRs")
```


```{r eval=FALSE, include=FALSE, echo=TRUE}
library(tidyverse)  # For dplyr, ggplot2, and friends
library(scriptuRs)  # For full text of bible
library(tidytext)   # For analyzing text
library(cleanNLP)   # For fancier natural language processing

# Load data
gospels <- kjv_bible() %>% 
  filter(book_title %in% c("Matthew", "Mark", "Luke", "John"))
```


```{r eval=FALSE, include=FALSE, echo=TRUE}
# Set up NLP backend
# reticulate::use_python("/Users/serdarbalciold/.conda")  # I use homebrew python3
# reticulate::use_condaenv(condaenv = "/anaconda3/envs", conda = "auto", required = FALSE)
# cnlp_init_spacy()  # Use spaCy
cnlp_init_udpipe()  # Or use this R-only one without external dependencies
```



```{r eval=FALSE, include=FALSE, echo=TRUE}
# Determine the parts of speech of the "text" column and use "verse_title" as the id
gospels_annotated <- cnlp_annotate(gospels, as_strings = TRUE,
                                   text_var = "text", doc_var = "verse_title")
```


```{r eval=FALSE, include=FALSE, echo=TRUE}
gospels_annotated
```


```{r eval=FALSE, include=FALSE, echo=TRUE}
glimpse(gospels_annotated)
```


```{r eval=FALSE, include=FALSE, echo=TRUE}
gospel_terms <- gospels_annotated %>% 
  cnlp_get_token()
head(gospel_terms)
```

```{r eval=FALSE, include=FALSE, echo=TRUE}
gospels_lookup <- gospels %>% 
  select(verse_title, book_title, chapter_number, verse_number)

gospel_terms <- gospel_terms %>% 
  left_join(gospels_lookup, by = c("id" = "verse_title"))

glimpse(gospel_terms)
```


# WORD ASSOCIATIONS FROM THE SMALL WORLD OF WORDS

https://juliasilge.com/blog/word-associations/


# 









