---
title: "Hypothesis Testing"
output: html_notebook
---

# Glue
Glue strings to data in R. Small, fast, dependency free interpreted string literals.

https://glue.tidyverse.org/

# infer package
Statistical Inference: A Tidy Approach
https://ismayc.github.io/talks/ness-infer/slide_deck.html

https://infer.netlify.com/

https://moderndive.netlify.com/

https://cran.r-project.org/web/packages/infer/index.html


# Hypothesis Testing

## Test Selection

### Statkat

https://statkat.com/

https://statkat.com/stattest_overview.php


#### Jamovi Statkat module

https://blog.jamovi.org/2018/06/25/statkat.html

```{r}
library(jmv)
library(Statkat)
```

```{r}

Statkat::correlational(
    data = data,
    dep = "len",
    independents = "supp")
```













# infer

Full infer pipeline examples using nycflights13 flights data


https://cran.r-project.org/web/packages/infer/vignettes/observed_stat_examples.html


Full infer pipeline examples using nycflights13 flights data
Chester Ismay
Updated on 2018-06-14
Data preparation
library(nycflights13)
library(dplyr)
library(ggplot2)
library(stringr)
library(infer)
set.seed(2017)
fli_small <- flights %>% 
  na.omit() %>%
  sample_n(size = 500) %>% 
  mutate(season = case_when(
    month %in% c(10:12, 1:3) ~ "winter",
    month %in% c(4:9) ~ "summer"
  )) %>% 
  mutate(day_hour = case_when(
    between(hour, 1, 12) ~ "morning",
    between(hour, 13, 24) ~ "not morning"
  )) %>% 
  select(arr_delay, dep_delay, season, 
         day_hour, origin, carrier)
Two numeric - arr_delay, dep_delay
Two categories
season ("winter", "summer"),
day_hour ("morning", "not morning")
Three categories - origin ("EWR", "JFK", "LGA")
Sixteen categories - carrier
Hypothesis tests
One numerical variable (mean)
Observed stat

( x_bar <- fli_small %>%
  specify(response = dep_delay) %>%
  calculate(stat = "mean") )
stat
10.4
null_distn <- fli_small %>%
  specify(response = dep_delay) %>%
  hypothesize(null = "point", mu = 10) %>%
  generate(reps = 1000) %>%
  calculate(stat = "mean")
## Setting `type = "bootstrap"` in `generate()`.
visualize(null_distn) +
  shade_p_value(obs_stat = x_bar, direction = "two_sided")

null_distn %>%
  get_p_value(obs_stat = x_bar, direction = "two_sided")
p_value
0.794
One numerical variable (standardized mean t)
Observed stat

( t_bar <- fli_small %>%
  specify(response = dep_delay) %>%
  calculate(stat = "t") )
stat
6.93
null_distn <- fli_small %>%
  specify(response = dep_delay) %>%
  hypothesize(null = "point", mu = 8) %>%
  generate(reps = 1000) %>%
  calculate(stat = "t")
## Setting `type = "bootstrap"` in `generate()`.
visualize(null_distn) +
  shade_p_value(obs_stat = t_bar, direction = "two_sided")

null_distn %>%
  get_p_value(obs_stat = t_bar, direction = "two_sided")
p_value
0
One numerical variable (median)
Observed stat

( x_tilde <- fli_small %>%
  specify(response = dep_delay) %>%
  calculate(stat = "median") )
stat
-2
null_distn <- fli_small %>%
  specify(response = dep_delay) %>%
  hypothesize(null = "point", med = -1) %>% 
  generate(reps = 1000) %>% 
  calculate(stat = "median")
## Setting `type = "bootstrap"` in `generate()`.
visualize(null_distn) +
  shade_p_value(obs_stat = x_tilde, direction = "two_sided")

null_distn %>%
  get_p_value(obs_stat = x_tilde, direction = "two_sided")
p_value
0.15
One categorical (one proportion)
Observed stat

( p_hat <- fli_small %>%
  specify(response = day_hour, success = "morning") %>%
  calculate(stat = "prop") )
stat
0.466
null_distn <- fli_small %>%
  specify(response = day_hour, success = "morning") %>%
  hypothesize(null = "point", p = .5) %>%
  generate(reps = 1000) %>%
  calculate(stat = "prop")
## Setting `type = "simulate"` in `generate()`.
visualize(null_distn) +
  shade_p_value(obs_stat = p_hat, direction = "two_sided")

null_distn %>%
  get_p_value(obs_stat = p_hat, direction = "two_sided")
p_value
0.11
Logical variables will be coerced to factors:

null_distn <- fli_small %>%
  mutate(day_hour_logical = (day_hour == "morning")) %>%
  specify(response = day_hour_logical, success = "TRUE") %>%
  hypothesize(null = "point", p = .5) %>%
  generate(reps = 1000) %>%
  calculate(stat = "prop")
## Setting `type = "simulate"` in `generate()`.
One categorical variable (standardized proportion z)
Not yet implemented.

Two categorical (2 level) variables
Observed stat

( d_hat <- fli_small %>% 
  specify(day_hour ~ season, success = "morning") %>%
  calculate(stat = "diff in props", order = c("winter", "summer")) )
stat
-0.0205
null_distn <- fli_small %>%
  specify(day_hour ~ season, success = "morning") %>%
  hypothesize(null = "independence") %>% 
  generate(reps = 1000) %>% 
  calculate(stat = "diff in props", order = c("winter", "summer"))
## Setting `type = "permute"` in `generate()`.
visualize(null_distn) +
  shade_p_value(obs_stat = d_hat, direction = "two_sided")

null_distn %>%
  get_p_value(obs_stat = d_hat, direction = "two_sided")
p_value
0.708
Two categorical (2 level) variables (z)
Standardized observed stat

( z_hat <- fli_small %>% 
  specify(day_hour ~ season, success = "morning") %>%
  calculate(stat = "z", order = c("winter", "summer")) )
stat
-0.4605
null_distn <- fli_small %>%
  specify(day_hour ~ season, success = "morning") %>%
  hypothesize(null = "independence") %>% 
  generate(reps = 1000) %>% 
  calculate(stat = "z", order = c("winter", "summer"))
## Setting `type = "permute"` in `generate()`.
visualize(null_distn) +
  shade_p_value(obs_stat = z_hat, direction = "two_sided")

null_distn %>%
  get_p_value(obs_stat = z_hat, direction = "two_sided")
p_value
0.684
Note the similarities in this plot and the previous one.

One categorical (>2 level) - GoF
Observed stat

Note the need to add in the hypothesized values here to compute the observed statistic.

( Chisq_hat <- fli_small %>%
  specify(response = origin) %>%
  hypothesize(null = "point", 
              p = c("EWR" = .33, "JFK" = .33, "LGA" = .34)) %>% 
  calculate(stat = "Chisq") )
stat
10.4
null_distn <- fli_small %>%
  specify(response = origin) %>%
  hypothesize(null = "point", 
              p = c("EWR" = .33, "JFK" = .33, "LGA" = .34)) %>% 
  generate(reps = 1000, type = "simulate") %>% 
  calculate(stat = "Chisq")

visualize(null_distn) +
  shade_p_value(obs_stat = Chisq_hat, direction = "greater")

null_distn %>%
  get_p_value(obs_stat = Chisq_hat, direction = "greater")
p_value
0.005
Two categorical (>2 level) variables
Observed stat

( Chisq_hat <- fli_small %>%
  specify(formula = day_hour ~ origin) %>% 
  calculate(stat = "Chisq") )
stat
9.027
null_distn <- fli_small %>%
  specify(day_hour ~ origin) %>%
  hypothesize(null = "independence") %>% 
  generate(reps = 1000, type = "permute") %>% 
  calculate(stat = "Chisq")

visualize(null_distn) +
  shade_p_value(obs_stat = Chisq_hat, direction = "greater")

null_distn %>%
  get_p_value(obs_stat = Chisq_hat, direction = "greater")
p_value
0.007
One numerical variable, one categorical (2 levels) (diff in means)
Observed stat

( d_hat <- fli_small %>% 
  specify(dep_delay ~ season) %>% 
  calculate(stat = "diff in means", order = c("summer", "winter")) )
stat
2.266
null_distn <- fli_small %>%
  specify(dep_delay ~ season) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("summer", "winter"))

visualize(null_distn) +
  shade_p_value(obs_stat = d_hat, direction = "two_sided")

null_distn %>%
  get_p_value(obs_stat = d_hat, direction = "two_sided")
p_value
0.488
One numerical variable, one categorical (2 levels) (t)
Standardized observed stat

( t_hat <- fli_small %>% 
  specify(dep_delay ~ season) %>% 
  calculate(stat = "t", order = c("summer", "winter")) )
stat
0.7542
null_distn <- fli_small %>%
  specify(dep_delay ~ season) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "t", order = c("summer", "winter"))

visualize(null_distn) +
  shade_p_value(obs_stat = t_hat, direction = "two_sided")

null_distn %>%
  get_p_value(obs_stat = t_hat, direction = "two_sided")
p_value
0.49
Note the similarities in this plot and the previous one.

One numerical variable, one categorical (2 levels) (diff in medians)
Observed stat

( d_hat <- fli_small %>% 
  specify(dep_delay ~ season) %>% 
  calculate(stat = "diff in medians", order = c("summer", "winter")) )
stat
2
null_distn <- fli_small %>%
  specify(dep_delay ~ season) %>% # alt: response = dep_delay, 
  # explanatory = season
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in medians", order = c("summer", "winter"))

visualize(null_distn) +
  shade_p_value(obs_stat = d_hat, direction = "two_sided")

null_distn %>%
  get_p_value(obs_stat = d_hat, direction = "two_sided")
p_value
0.084
One numerical, one categorical (>2 levels) - ANOVA
Observed stat

( F_hat <- fli_small %>% 
  specify(arr_delay ~ origin) %>%
  calculate(stat = "F") )
stat
1.084
null_distn <- fli_small %>%
   specify(arr_delay ~ origin) %>%
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
   calculate(stat = "F")

visualize(null_distn) +
  shade_p_value(obs_stat = F_hat, direction = "greater")

null_distn %>%
  get_p_value(obs_stat = F_hat, direction = "greater")
p_value
0.353
Two numerical vars - SLR
Observed stat

( slope_hat <- fli_small %>% 
  specify(arr_delay ~ dep_delay) %>% 
  calculate(stat = "slope") )
stat
1.017
null_distn <- fli_small %>%
   specify(arr_delay ~ dep_delay) %>% 
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
   calculate(stat = "slope")

visualize(null_distn) +
  shade_p_value(obs_stat = slope_hat, direction = "two_sided")

null_distn %>%
  get_p_value(obs_stat = slope_hat, direction = "two_sided")
p_value
0
Two numerical vars - correlation
Observed stat

( correlation_hat <- fli_small %>% 
  specify(arr_delay ~ dep_delay) %>% 
  calculate(stat = "correlation") )
stat
0.8943
null_distn <- fli_small %>%
   specify(arr_delay ~ dep_delay) %>% 
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
   calculate(stat = "correlation")

visualize(null_distn) +
  shade_p_value(obs_stat = correlation_hat, direction = "two_sided")

null_distn %>%
  get_p_value(obs_stat = correlation_hat, direction = "two_sided")
p_value
0
Two numerical vars - SLR (t)
Not currently implemented since t could refer to standardized slope or standardized correlation.

Confidence intervals
One numerical (one mean)
Point estimate

( x_bar <- fli_small %>% 
  specify(response = arr_delay) %>%
  calculate(stat = "mean") )
stat
4.572
boot <- fli_small %>%
   specify(response = arr_delay) %>%
   generate(reps = 1000, type = "bootstrap") %>%
   calculate(stat = "mean")
( percentile_ci <- get_ci(boot) )
2.5%	97.5%
1.436	7.819
visualize(boot) +
  shade_confidence_interval(endpoints = percentile_ci)

( standard_error_ci <- get_ci(boot, type = "se", point_estimate = x_bar) )
lower	upper
1.267	7.877
visualize(boot) +
  shade_confidence_interval(endpoints = standard_error_ci)

One numerical (one mean - standardized)
Point estimate

( t_hat <- fli_small %>% 
  specify(response = arr_delay) %>%
  calculate(stat = "t") )
stat
2.679
boot <- fli_small %>%
   specify(response = arr_delay) %>%
   generate(reps = 1000, type = "bootstrap") %>%
   calculate(stat = "t")
( percentile_ci <- get_ci(boot) )
2.5%	97.5%
0.9338	4.362
visualize(boot) +
  shade_confidence_interval(endpoints = percentile_ci)

( standard_error_ci <- get_ci(boot, type = "se", point_estimate = t_hat) )
lower	upper
0.9141	4.444
visualize(boot) +
  shade_confidence_interval(endpoints = standard_error_ci)

One categorical (one proportion)
Point estimate

( p_hat <- fli_small %>% 
   specify(response = day_hour, success = "morning") %>%
   calculate(stat = "prop") )
stat
0.466
boot <- fli_small %>%
 specify(response = day_hour, success = "morning") %>%
 generate(reps = 1000, type = "bootstrap") %>%
 calculate(stat = "prop")
( percentile_ci <- get_ci(boot) )
2.5%	97.5%
0.42	0.508
visualize(boot) +
  shade_confidence_interval(endpoints = percentile_ci)

( standard_error_ci <- get_ci(boot, type = "se", point_estimate = p_hat) )
lower	upper
0.4218	0.5102
visualize(boot) +
  shade_confidence_interval(endpoints = standard_error_ci)

One categorical variable (standardized proportion z)
Not yet implemented.

One numerical variable, one categorical (2 levels) (diff in means)
Point estimate

( d_hat <- fli_small %>%
  specify(arr_delay ~ season) %>%
  calculate(stat = "diff in means", order = c("summer", "winter")) )
stat
-0.7452
boot <- fli_small %>%
   specify(arr_delay ~ season) %>%
   generate(reps = 1000, type = "bootstrap") %>%
   calculate(stat = "diff in means", order = c("summer", "winter"))
( percentile_ci <- get_ci(boot) )
2.5%	97.5%
-7.167	6.079
visualize(boot) +
  shade_confidence_interval(endpoints = percentile_ci)

( standard_error_ci <- get_ci(boot, type = "se", point_estimate = d_hat) )
lower	upper
-7.296	5.806
visualize(boot) +
  shade_confidence_interval(endpoints = standard_error_ci)

One numerical variable, one categorical (2 levels) (t)
Standardized point estimate

( t_hat <- fli_small %>%
  specify(arr_delay ~ season) %>%
  calculate(stat = "t", order = c("summer", "winter")) )
stat
-0.2182
boot <- fli_small %>%
   specify(arr_delay ~ season) %>%
   generate(reps = 1000, type = "bootstrap") %>%
   calculate(stat = "t", order = c("summer", "winter"))
( percentile_ci <- get_ci(boot) )
2.5%	97.5%
-2.236	1.718
visualize(boot) +
  shade_confidence_interval(endpoints = percentile_ci)

( standard_error_ci <- get_ci(boot, type = "se", point_estimate = t_hat) )
lower	upper
-2.183	1.746
visualize(boot) +
  shade_confidence_interval(endpoints = standard_error_ci)

Two categorical variables (diff in proportions)
Point estimate

( d_hat <- fli_small %>% 
  specify(day_hour ~ season, success = "morning") %>%
  calculate(stat = "diff in props", order = c("summer", "winter")) )
stat
0.0205
boot <- fli_small %>%
  specify(day_hour ~ season, success = "morning") %>%
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "diff in props", order = c("summer", "winter"))
( percentile_ci <- get_ci(boot) )
2.5%	97.5%
-0.0648	0.1083
visualize(boot) +
  shade_confidence_interval(endpoints = percentile_ci)

( standard_error_ci <- get_ci(boot, type = "se", point_estimate = d_hat) )
lower	upper
-0.0676	0.1087
visualize(boot) +
  shade_confidence_interval(endpoints = standard_error_ci)

Two categorical variables (z)
Standardized point estimate

( z_hat <- fli_small %>% 
  specify(day_hour ~ season, success = "morning") %>%
  calculate(stat = "z", order = c("summer", "winter")) )
stat
0.4605
boot <- fli_small %>%
  specify(day_hour ~ season, success = "morning") %>%
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "z", order = c("summer", "winter"))
( percentile_ci <- get_ci(boot) )
2.5%	97.5%
-1.479	2.501
visualize(boot) +
  shade_confidence_interval(endpoints = percentile_ci)

( standard_error_ci <- get_ci(boot, type = "se", point_estimate = z_hat) )
lower	upper
-1.522	2.443
visualize(boot) +
  shade_confidence_interval(endpoints = standard_error_ci)

Two numerical vars - SLR
Point estimate

( slope_hat <- fli_small %>% 
  specify(arr_delay ~ dep_delay) %>%
  calculate(stat = "slope") )
stat
1.017
boot <- fli_small %>%
   specify(arr_delay ~ dep_delay) %>% 
   generate(reps = 1000, type = "bootstrap") %>%
   calculate(stat = "slope")
( percentile_ci <- get_ci(boot) )
2.5%	97.5%
0.9728	1.074
visualize(boot) +
  shade_confidence_interval(endpoints = percentile_ci)

( standard_error_ci <- get_ci(boot, type = "se", point_estimate = slope_hat) )
lower	upper
0.9653	1.069
visualize(boot) +
  shade_confidence_interval(endpoints = standard_error_ci)

Two numerical vars - correlation
Point estimate

( correlation_hat <- fli_small %>% 
  specify(arr_delay ~ dep_delay) %>%
  calculate(stat = "correlation") )
stat
0.8943
boot <- fli_small %>%
   specify(arr_delay ~ dep_delay) %>% 
   generate(reps = 1000, type = "bootstrap") %>%
   calculate(stat = "correlation")
( percentile_ci <- get_ci(boot) )
2.5%	97.5%
0.8502	0.9218
visualize(boot) +
  shade_confidence_interval(endpoints = percentile_ci)

( standard_error_ci <- get_ci(boot, type = "se", 
                            point_estimate = correlation_hat) )
lower	upper
0.858	0.9306
visualize(boot) +
  shade_confidence_interval(endpoints = standard_error_ci)

Two numerical vars - t
Not currently implemented since t could refer to standardized slope or standardized correlation.



